---
title: "data-anlaysis"
author: "Kunlei He"
date: "2025-03-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

# Load library
```{r}
library(dplyr)
library(ggplot2)
library(lavaan)  # For FIML estimation
library(lmtest)  # For robust standard errors
library(sandwich)  # For clustered standard errors
library(dplyr)
library(emmeans)
library(mice)
library(miceadds)
library(cobalt)
library(MatchIt)
library(lmerTest)
```


# Load data
```{r}
df_wide <- read.csv("processed_data/full_data_wide.csv")
df_long_post <- read.csv("processed_data/full_data_long_post.csv")
df_long_delayed <- read.csv("processed_data/full_data_long_delayed.csv")
```

# Resolve sample imbalance
```{r}
# check the unbalance before matching
bal.tab(CA ~ age, data = df_wide)

# Use propensity score matching
df_wide$CA <- as.factor(df_wide$CA)

# Perform propensity score matching
# The formula specifies that 'CA' is the treatment and 'age' is the covariate
# remove ids with missing MEFS
psm_model <- matchit(CA ~ age, data = df_wide, method = "nearest", caliper = 0.3)

# Create a matched data frame
df_wide_balanced <- match.data(psm_model)

# check balance after matching
bal.tab(psm_model)

# check age balance
## get the mean, min, max for age by CA
df_wide_balanced %>%
  group_by(CA) %>%
  summarise(mean_age = mean(age), min_age = min(age), max_age = max(age))

model <- aov(age ~ CA, data = df_wide_balanced)
summary(model)

model <- aov(QUILS_score ~ CA, data = df_wide_balanced)
summary(model)

model <- aov(lens_score ~ CA, data = df_wide_balanced)
summary(model)

model <- aov(MEFS_score ~ CA, data = df_wide_balanced)
summary(model)
```

```{r}
# convert balanced wide data into long form
df_wide_selected_post <- df_wide_balanced %>%
  # First, select columns that remain unchanged for each participant
  select(id, age, gender, ethnicity, location, CA, lens_score, 
         QUILS_score, ToM_total_score, MEFS_score, pretest_score,
         # Select episode-specific columns with more precise matching
         matches("^condition\\d+$"), 
         matches("^ep\\d+_notes$"),
         matches("^ep\\d+_posttest_date$"),
         matches("^p\\d+_ra$"),
         matches("^p\\d+_total_score$"),
         matches("^p\\d+_total_score_z$")) %>% 
  # Rename condition columns to have a consistent pattern with other columns
  rename(
    condition_117 = condition117,
    condition_109 = condition109,
    condition_101 = condition101,
    notes_117 = ep117_notes,
    notes_109 = ep109_notes,
    notes_101 = ep101_notes,
    date_117 = ep117_posttest_date,
    date_109 = ep109_posttest_date,
    date_101 = ep101_posttest_date,
    ra_109 = p109_ra,
    ra_117 = p117_ra,
    ra_101 = p101_ra,
    total_score_109 = p109_total_score,
    total_score_117 = p117_total_score,
    total_score_101 = p101_total_score,
    total_score_z_109 = p109_total_score_z,
    total_score_z_117 = p117_total_score_z,
    total_score_z_101 = p101_total_score_z
  )

# Now transform to long format
df_long_post_matched <- df_wide_selected_post %>% 
  # Pivot to long format
  pivot_longer(
    # Columns to pivot
    cols = c(
      starts_with("condition_"),
      starts_with("notes_"),
      starts_with("date_"),
      starts_with("ra_"),
      starts_with("total_score_") & !starts_with("total_score_z_"),
      starts_with("total_score_z_")
    ),
    
    # Extract episode number and variable type
    names_to = c(".value", "episode"),
    
    # Pattern for matching: varname_episode
    names_pattern = "(.+)_(\\d+)",
    
    # Don't include NA values
    values_drop_na = FALSE
  ) %>%
  
  # Rename the date column to posttest_date
  rename(posttest_date = date) %>%
  
  # Select final columns in requested order
  select(id, episode, age, gender, ethnicity, location, CA, lens_score, 
         QUILS_score, ToM_total_score, MEFS_score, pretest_score,
         condition, total_score, total_score_z, posttest_date, notes, ra)

df_long_post_matched$test_type = "post"

# re-order columns
df_long_post_matched <- df_long_post_matched %>% 
  select(id, episode, condition, test_type, everything())
```

```{r}
df_wide_selected_delayed <- df_wide_balanced %>%
  # First, select columns that remain unchanged for each participant
  select(id, age, gender, ethnicity, location, CA, lens_score, 
         QUILS_score, ToM_total_score, MEFS_score, pretest_score,
         # Select episode-specific columns with more precise matching
         condition109, condition117, 
         d109_ra, d117_ra,
         d109_total_score, d109_total_score_z,
         d117_total_score, d117_total_score_z)%>% 
  # Rename condition columns to have a consistent pattern with other columns
  rename(
    condition_117 = condition117,
    condition_109 = condition109,
    ra_109 = d109_ra,
    ra_117 = d117_ra,,
    total_score_109 = d109_total_score,
    total_score_117 = d117_total_score,
    total_score_z_109 = d109_total_score_z,
    total_score_z_117 = d117_total_score_z,
  )

# Now transform to long format
df_long_delayed_matched <- df_wide_selected_delayed %>% 
  # Pivot to long format
  pivot_longer(
    # Columns to pivot
    cols = c(
      starts_with("condition_"),
      starts_with("ra_"),
      starts_with("total_score_") & !starts_with("total_score_z_"),
      starts_with("total_score_z_")
    ),
    
    # Extract episode number and variable type
    names_to = c(".value", "episode"),
    
    # Pattern for matching: varname_episode
    names_pattern = "(.+)_(\\d+)",
    
    # Don't include NA values
    values_drop_na = FALSE
  ) %>%
  
  # Select final columns in requested order
  select(id, episode, age, gender, ethnicity, location, CA, lens_score, 
         QUILS_score, ToM_total_score, MEFS_score, pretest_score,
         condition, total_score, total_score_z, ra)

df_long_delayed_matched$test_type = "delayed"

# re-order columns
df_long_delayed_matched <- df_long_delayed_matched %>% 
  select(id, episode, condition, test_type, everything())
```


# Data processing
### Immediate post-test
```{r}
# Factor variables
## factor condition, set interactive as reference
df_long_post$condition <- factor(df_long_post$condition, levels = c("interactive", "no", "semi", "human"))
df_long_post_matched$condition <- factor(df_long_post_matched$condition, levels = c("interactive", "no", "semi", "human"))

## factor episode, test_type, gender, ethnicity, location, CA
df_long_post$episode <- factor(df_long_post$episode)
df_long_post$test_type <- factor(df_long_post$test_type)
df_long_post$gender <- factor(df_long_post$gender)
df_long_post$ethnicity <- factor(df_long_post$ethnicity)
df_long_post$location <- factor(df_long_post$location)
df_long_post$CA <- factor(df_long_post$CA)
```

```{r}
# Create dummy variables for condition
df_long_post$no <- ifelse(df_long_post$condition == "no", 1, 0)
df_long_post$semi <- ifelse(df_long_post$condition == "semi", 1, 0)
df_long_post$human <- ifelse(df_long_post$condition == "human", 1, 0)
df_long_post$interactive <- ifelse(df_long_post$condition == "interactive", 1, 0)

# Create dummy variables for gender
df_long_post$male <- ifelse(df_long_post$gender == "male", 1, 0)
df_long_post$female <- ifelse(df_long_post$gender == "female", 1, 0)

# Create dummy variables for ethnicity
df_long_post$hispanic <- ifelse(df_long_post$ethnicity == "hispanic", 1, 0)
df_long_post$not_hispanic <- ifelse(df_long_post$ethnicity == "notHispanic", 1, 0)
```


### Delayed post-test
```{r}
# Factor variables
## factor condition, set interactive as reference
df_long_delayed$condition <- factor(df_long_delayed$condition, levels = c("interactive", "no", "semi", "human"))
df_long_delayed_matched$condition <- factor(df_long_delayed_matched$condition, levels = c("interactive", "no", "semi", "human"))
```

# Data anlaysis
## Immediate post-test
### Full sample, no controls
```{r}
model_full_no_control <- lmer(total_score_z ~ condition + (1|id), data = df_long_post)
summary(model_full_no_control)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_full_no_control)
summary(model_test)


# get the number of unique id each condition
df_long_post %>%
  filter(!is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))
```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_full_no_control, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=66)","Human-\nInteractive\n(N=55)", "Pseudo-\ninteractive\n(N=53)", "Non-\nInteractive\n(N=57)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on immediate post-test scores \n(no covariates, full sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-immediate-full-no-controls.png", width = 7, height = 6, dpi = 300)
```

### Full sample, with controls
```{r}
model_full_with_controls <- lmer(total_score_z ~ condition + age + gender + ethnicity + lens_score + QUILS_score + MEFS_score + ToM_total_score + pretest_score + (1|id), data = df_long_post)
summary(model_full_with_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_full_with_controls)
summary(model_test)


# get the number of participant each group with no missing data in all the baseline measures
df_long_post %>%
  filter(!is.na(age) & !is.na(gender) & !is.na(ethnicity) & !is.na(lens_score) & !is.na(QUILS_score) & !is.na(MEFS_score) & !is.na(ToM_total_score) & !is.na(pretest_score) & !is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point

# Get estimated marginal means for condition
emm_condition <- emmeans(model_full_with_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))

ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=60)","Human-\nInteractive\n(N=47)", "Pseudo-\ninteractive\n(N=44)", "Non-\nInteractive\n(N=48)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on immediate post-test scores \n(with covariates, full sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-immediate-full-with-controls.png", width = 7, height = 6, dpi = 300)
```
### Balanced sample, no controls
```{r}
model_balanced_no_controls <- lmer(total_score_z ~ condition + (1|id), data = df_long_post_matched)
summary(model_balanced_no_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_balanced_no_controls)
summary(model_test)

df_long_post_matched %>%
  filter(!is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_balanced_no_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=50)","Human-\nInteractive\n(N=45)", "Pseudo-\ninteractive\n(N=43)", "Non-\nInteractive\n(N=47)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on immediate post-test scores \n(no covariates, balanced sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-immediate-balanced-no-controls.png", width = 7, height = 6, dpi = 300)
```
### Balanced sample, with controls
```{r}
model_balanced_with_controls <- lmer(total_score_z ~ condition + age + gender + ethnicity + lens_score + QUILS_score + MEFS_score + ToM_total_score + pretest_score + (1|id), data = df_long_post_matched)
summary(model_balanced_with_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_balanced_with_controls)
summary(model_test)

df_long_post_matched %>%
  filter(!is.na(age) & !is.na(gender) & !is.na(ethnicity) & !is.na(lens_score) & !is.na(QUILS_score) & !is.na(MEFS_score) & !is.na(ToM_total_score) & !is.na(pretest_score) & !is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_balanced_with_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=44)","Human-\nInteractive\n(N=39)", "Pseudo-\ninteractive\n(N=36)", "Non-\nInteractive\n(N=40)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on immediate post-test scores \n(with covariates, balanced sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-immediate-balanced-with-controls.png", width = 7, height = 6, dpi = 300)
```
## Delayed post-test
### Full sample, no controls
```{r}
model_full_no_control <- lmer(total_score_z ~ condition + (1|id), data = df_long_delayed)
summary(model_full_no_control)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_full_no_control)
summary(model_test)


# get the number of unique id each condition
df_long_delayed %>%
  filter(!is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))
```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_full_no_control, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=66)","Human-\nInteractive\n(N=35)", "Pseudo-\ninteractive\n(N=31)", "Non-\nInteractive\n(N=43)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on delayed post-test scores \n(no covariates, full sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-delayed-full-no-controls.png", width = 7, height = 6, dpi = 300)
```

### Full sample, with controls
```{r}
model_full_with_controls <- lmer(total_score_z ~ condition + age + gender + ethnicity + lens_score + QUILS_score + MEFS_score + ToM_total_score + pretest_score + (1|id), data = df_long_delayed)
summary(model_full_with_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_full_with_controls)
summary(model_test)


# get the number of participant each group with no missing data in all the baseline measures
df_long_delayed %>%
  filter(!is.na(age) & !is.na(gender) & !is.na(ethnicity) & !is.na(lens_score) & !is.na(QUILS_score) & !is.na(MEFS_score) & !is.na(ToM_total_score) & !is.na(pretest_score) & !is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point

# Get estimated marginal means for condition
emm_condition <- emmeans(model_full_with_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))

ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=60)","Human-\nInteractive\n(N=29)", "Pseudo-\ninteractive\n(N=28)", "Non-\nInteractive\n(N=36)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on delayed post-test scores \n(with covariates, full sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-delayed-full-with-controls.png", width = 7, height = 6, dpi = 300)
```
### Balanced sample, no controls
```{r}
model_balanced_no_controls <- lmer(total_score_z ~ condition + (1|id), data = df_long_delayed_matched)
summary(model_balanced_no_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_balanced_no_controls)
summary(model_test)

df_long_delayed_matched %>%
  filter(!is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_balanced_no_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=50)","Human-\nInteractive\n(N=28)", "Pseudo-\ninteractive\n(N=24)", "Non-\nInteractive\n(N=37)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on delayed post-test scores \n(no covariates, balanced sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-delayed-balanced-no-controls.png", width = 7, height = 6, dpi = 300)
```
### Balanced sample, with controls
```{r}
model_balanced_with_controls <- lmer(total_score_z ~ condition + age + gender + ethnicity + lens_score + QUILS_score + MEFS_score + ToM_total_score + pretest_score + (1|id), data = df_long_delayed_matched)
summary(model_balanced_with_controls)

# get the p-value for each of the coefficients
model_test <- lmerTest::as_lmerModLmerTest(model_balanced_with_controls)
summary(model_test)

df_long_delayed_matched %>%
  filter(!is.na(age) & !is.na(gender) & !is.na(ethnicity) & !is.na(lens_score) & !is.na(QUILS_score) & !is.na(MEFS_score) & !is.na(ToM_total_score) & !is.na(pretest_score) & !is.na(total_score_z)) %>%
  group_by(condition) %>%
  summarise(n = n_distinct(id))

```

```{r}
# draw a plot of the mixed-effects model, x-axis is the condition, y-axis is the coefficients, and the error bar is the standard error, represent the coefficents using a point
emm_condition <- emmeans(model_balanced_with_controls, ~ condition)
emm_df <- as.data.frame(emm_condition)
emm_df$condition <- factor(emm_df$condition, 
                           levels = c("interactive", "human", "semi", "no"))


ggplot(emm_df, aes(x = condition, y = emmean, color = condition)) +
  geom_point(size = 5, show.legend = FALSE) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, colour="#404040", alpha=0.8) +
  scale_x_discrete(labels=c("CA-\nInteractive\n(N=44)","Human-\nInteractive\n(N=23)", "Pseudo-\ninteractive\n(N=22)", "Non-\nInteractive\n(N=32)")) +
  scale_color_manual(name="Condition", values = c("#F97B22", "#7AA874","#6096B4", "gray")) +
  labs(
    title = "Predicted effects of condition on delayed post-test scores \n(with covariates, balanced sample)",
    x = "",
    y = "Predicted scores"
  ) +
  theme_classic() +
  theme(legend.title=element_blank()) +
  theme(panel.grid.major.y = element_line()) +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size=14, color="black"),
        plot.title = element_text(hjust = 0.5))

# save
ggsave("figures/main-effect-delayed-balanced-with-controls.png", width = 7, height = 6, dpi = 300)
```

