---
title: "AISL2_EWW_data_prep"
author: "Kunlei He"
date: "2024-02-17"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    toc_collapse: true
    number_sections: true
    df_print: paged
    theme: lumen
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

# Load library
```{r}
library(openxlsx)
library(dplyr)
library(lme4)
library(ggplot2)
library(tidyr)
```

# Load data
```{r}
df_RawTracker = read.xlsx("raw_data/raw_tracker.xlsx")

df_QuilsPt1 = read.csv("raw_data/raw_quils_pt1.csv")
df_QuilsPt2 = read.csv("raw_data/raw_quils_pt2.csv")

df_RawPost117 = read.csv("raw_data/raw_post_117.csv")
df_RawPost109 = read.csv("raw_data/raw_post_109.csv")
df_RawPost101 = read.csv("raw_data/raw_post_101.csv")


df_RawDelayed117 = read.csv("raw_data/raw_delayed_post_117.csv")
df_RawDelayed109 = read.csv("raw_data/raw_delayed_post_109.csv")
```

# Clean data
## Tracker
```{r}
# remove the first row
names(df_RawTracker) = as.character(unlist(df_RawTracker[1, ]))  # Set the first row as names
df_RawTracker = df_RawTracker[-1, ]  # Remove the first row from the data

# only keep useful columnns
cols = c("id", "condition", "dob", "gender", "ethnicity", "race", "condition117","ep117_posttest_date", "ep117_notes", "condition109", "ep109_posttest_date","ep109_notes", "condition101", "ep101_posttest_date", "ep101_notes")
df_Tracker = df_RawTracker[, cols]

# convert dates
dateCols = c("dob","ep117_posttest_date", "ep109_posttest_date", "ep101_posttest_date")
df_Tracker[dateCols] = lapply(df_Tracker[dateCols], function(x) as.Date(as.numeric(x), origin = "1899-12-30"))

# remove id if child did zero sessions
df_Tracker = df_Tracker %>%  filter(!is.na(ep117_posttest_date) | !is.na(ep109_posttest_date) | !is.na(ep101_posttest_date))

# rename condition as CA
df_Tracker <- df_Tracker %>%
  rename(CA = condition)

# check the range of ids for future use
print(range(df_Tracker$id))
```
### check dup rows
```{r}
dupRows <- df_Tracker %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows)
```

### fix conditions
```{r}
# For id = 3453, change condition117 to "human"
df_Tracker$condition117[df_Tracker$id == "3453"] = "human"

# For id = 3864 and id = 3687, change condition117 to "interactive"
df_Tracker$condition117[df_Tracker$id == "3684"] = "interactive"
df_Tracker$condition117[df_Tracker$id == "3687"] = "interactive"

# For id = 3719, change condition 117 to "no
df_Tracker$condition117[df_Tracker$id == "3719"] = "interactive"

# For id = 3469, change condition109 to "human"
df_Tracker$condition109[df_Tracker$id == "3469"] = "human"

# For id = 3260, change condition109 to "interactive"
df_Tracker$condition109[df_Tracker$id == "3260"] = "interactive"

# For id = 3469, change condition101 to "no"
df_Tracker$condition101[df_Tracker$id == "3469"] = "no"



```

### clean age and ethnicity
```{r}
# age
# Ensure both dob and ep117_posttest_date are in Date format
df_Tracker$dob = as.Date(df_Tracker$dob)
df_Tracker$ep117_posttest_date = as.Date(df_Tracker$ep117_posttest_date)

# Calculate age 
df_Tracker$age = as.numeric(df_Tracker$ep117_posttest_date - df_Tracker$dob)/365.25

# Optionally, you might want to round the age to a reasonable number of decimal places
df_Tracker$age <- round(df_Tracker$age, 2)

# rearrange
df_Tracker = df_Tracker %>% dplyr::select(id, age, gender, ethnicity, everything())

# ethnicity
table(df_Tracker$ethnicity)
df_Tracker$ethnicity = ifelse(is.na(df_Tracker$ethnicity), NA, 
                              ifelse(grepl("not", df_Tracker$ethnicity), "notHispanic", "hispanic"))
```
## Quils
### check dup rows
```{r}
# row bind quils pt1 and pt2
df_Quils = rbind(df_QuilsPt1, df_QuilsPt2)
# rename id
df_Quils = df_Quils %>% rename(id = Student.ID)

# check dup rows
dupRows <- df_Quils %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows)

```
### remove dup rows
```{r}
df_Quils$First.Access <- as.POSIXct(df_Quils$First.Access, format="%m/%d/%Y %H:%M", tz="UTC")


# Sort by 'id' and 'First.Access' in descending order within each 'id', then keep the last occurrence
df_Quils <- df_Quils %>%
  arrange(id, First.Access) %>%
  filter(!duplicated(id, fromLast = TRUE))

# check dup rows again
dupRows <- df_Quils %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows)

```

### score
```{r}
correctAnswers = c(1,3,2,2,1, #q1-q5
                      1,3,3,1, # q6-q9
                      2,3,3,1, # q10-q13
                      3,1,3, # q14-q16
                      2,1, # q17-q18
                      4,2,1,3, # q19-q22
                      4,3,1, # q23-q25
                      3,1,2,1,1, # q26-q30
                      4,3, # q31
                      2,3, # q32
                      4,1, # q33
                      2,4, # q34
                      3,2, # q35
                      2,2,3,1,3, # q36-q40
                      2,1, # q41
                      1,2, # q42
                      3,3, # q43
                      1,3, # q44
                      2,3, # q45
                      2,3,1 # q46-q48
                      ) 

# calculate scores by item
for(i in 1:length(correctAnswers)){
  questionColName = colnames(df_Quils)[12 + i] # Adjusting index to match question columns
  scoreColName <- paste0(questionColName, "_score")
  df_Quils[[scoreColName]] <- ifelse(df_Quils[[questionColName]] == correctAnswers[i], 1, 0)
}

# calcualte sum score
scoreCols <- grep("_score$", names(df_Quils), value = TRUE)
df_Quils$eng_prof <- rowSums(df_Quils[, scoreCols], na.rm = TRUE)


# merge to tracker
df_Tracker = merge(df_Tracker, df_Quils[, c("id", "eng_prof")], by=c("id"), all.x=T)

# rearrange
df_Tracker = df_Tracker %>% dplyr::select(id, age, gender, ethnicity, eng_prof, everything())

# check dup rows
dupRows <- df_Tracker %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows)
```


## Episode 117 post and delayed
Post 117
```{r}
# remove unuseful columns
df_Post117 = df_RawPost117[, -c(2:17)]

# remove first two rows
df_Post117 = df_Post117[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Post117$id = ifelse(df_Post117$Intro_4 %in% c(3000:4000), df_Post117$Intro_4, df_Post117$Intro_5)
# get the ra initials
df_Post117$ra = ifelse(is.na(as.numeric(as.character(df_Post117$Intro_4))), df_Post117$Intro_4, df_Post117$Intro_5)
# get rid of intro_4 and intro_5
df_Post117 = df_Post117 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Post117 = df_Post117 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Post117 = df_Post117 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post117$id that are NOT present in df_Tracker$id
diffID = df_Post117$id[!df_Post117$id %in% df_Tracker$id]
print(diffID) # check with Kelsy (see notes.md)
```

Delayed 117
```{r}
# remove unuseful columns
df_Delayed117 = df_RawDelayed117[, -c(2:17)]

# remove first two rows
df_Delayed117 = df_Delayed117[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Delayed117$id = ifelse(df_Delayed117$Intro_4 %in% c(3000:4000), df_Delayed117$Intro_4, df_Delayed117$Intro_5)
# get the ra initials
df_Delayed117$ra = ifelse(is.na(as.numeric(as.character(df_Delayed117$Intro_4))), df_Delayed117$Intro_4, df_Delayed117$Intro_5)
# get rid of intro_4 and intro_5
df_Delayed117 = df_Delayed117 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Delayed117 = df_Delayed117 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Delayed117 = df_Delayed117 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post117$id that are NOT present in df_Tracker$id
diffID = as.numeric(df_Delayed117$id[!df_Delayed117$id %in% df_Tracker$id])
print(diffID) 
```

## Episode 109 post and delayed
post
```{r}
# remove unuseful columns
df_Post109 = df_RawPost109[, -c(2:17)]


# remove first two rows
df_Post109 = df_Post109[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Post109$id = ifelse(df_Post109$Intro_4 %in% c(3000:4000), df_Post109$Intro_4, df_Post109$Intro_5)
# get the ra initials
df_Post109$ra = ifelse(is.na(as.numeric(as.character(df_Post109$Intro_4))), df_Post109$Intro_4, df_Post109$Intro_5)
# get rid of intro_4 and intro_5
df_Post109 = df_Post109 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Post109 = df_Post109 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Post109 = df_Post109 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post109$id that are NOT present in df_Tracker$id
diffID = as.numeric(df_Post109$id[!df_Post109$id %in% df_Tracker$id])
print(diffID) 

# check if they were before the shutdown
print(df_Post109[df_Post109$id %in% diffID, ])
```
Delayed
```{r}
# remove unuseful columns
df_Delayed109 = df_RawDelayed109[, -c(2:17)]

# remove first two rows
df_Delayed109 = df_Delayed109[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Delayed109$id = ifelse(df_Delayed109$Intro_4 %in% c(3000:4000), df_Delayed109$Intro_4, df_Delayed109$Intro_5)
# get the ra initials
df_Delayed109$ra = ifelse(is.na(as.numeric(as.character(df_Delayed109$Intro_4))), df_Delayed109$Intro_4, df_Delayed109$Intro_5)
# get rid of intro_4 and intro_5
df_Delayed109 = df_Delayed109 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Delayed109 = df_Delayed109 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Delayed109 = df_Delayed109 %>%  filter(id %in% c(3000:4000))

# find elements in df_Tracker$id that are NOT present in df_Post109$id
diffID = as.numeric(df_Tracker$id[!df_Tracker$id %in% df_Delayed109$id])
print(diffID) 
# check the tracker
print(df_RawTracker[df_RawTracker$id %in% diffID, ])
```

## Episode 101 post 
post
```{r}
# remove unuseful columns
df_Post101 = df_RawPost101[, -c(2:17)]

# remove first two rows
df_Post101 = df_Post101[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Post101$id = ifelse(df_Post101$Intro_4 %in% c(3000:4000), df_Post101$Intro_4, df_Post101$Intro_5)
# get the ra initials
df_Post101$ra = ifelse(is.na(as.numeric(as.character(df_Post101$Intro_4))), df_Post101$Intro_4, df_Post101$Intro_5)
# get rid of intro_4 and intro_5
df_Post101 = df_Post101 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Post101 = df_Post101 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Post101 = df_Post101 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post101$id that are NOT present in df_Tracker$id
diffID = df_Post101$id[!df_Post101$id %in% df_Tracker$id]
print(diffID) # check with Kelsy (see notes.md)
```

# Rename, check dup, and  score data
1. Rename and score post and delayed since they share same columns
2. Check dup rows
3. Rename colnames again to specify post and delayed by adding prefix

## Episode 117 post and delayed
Rename
```{r}
# print(colnames(df_Post117))
# print(head(df_Post117))

# set up colume names for 117
colNames117 = c("id", "ra", "start_date", 
                "q1_init_choice", "q1_init_text", "q1_rpt_choice", "q1_rpt_text",
                "q2_init_choice", "q2_init_text", "q2_rpt_choice", "q2_rpt_text",
                "q3_init_choice", "q3_init_text", "q3_rpt_choice", "q3_rpt_text",
                "q4_cr",
                "q5a_init_choice", "q5a_init_text", "q5b_init_choice", "q5b_init_text",
                "q6_init_choice", "q6_init_text", "q6_rpt_choice", "q6_rpt_text",
                "q7_init_choice", "q7_init_text", "q7_rpt_choice", "q7_rpt_text",
                "q8_init_choice", "q8_init_text", "q8_rpt_choice", "q8_rpt_text",
                "q9_init_choice", "q9_init_text", "q9_rpt_choice", "q9_rpt_text",
                "q10_init_choice", "q10_init_text", "q10_rpt_choice", "q10_rpt_text",
                "q11_init_choice", "q11_init_text", "q11_rpt_choice", "q11_rpt_text",
                "q12_init_choice", "q12_init_text", "q12_rpt_choice", "q12_rpt_text",
                "q13_init_choice", "q13_init_text", "q13_rpt_choice", "q13_rpt_text",
                "q14_init_choice", "q14_init_text", "q14_rpt_choice", "q14_rpt_text",
                "q15_cr", "notes"
)

# rename
colnames(df_Post117) = colNames117
colnames(df_Delayed117) = colNames117

# convert id to be numeric
df_Post117$id = as.numeric(df_Post117$id)
df_Delayed117$id = as.numeric(df_Delayed117$id)
```

### Check duplicated rows 117
```{r}
dupRows_Post117 <- df_Post117 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post117)

dupRows_Delayed117 <- df_Delayed117 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()


print(dupRows_Delayed117)
```
clean dup rows post 117
```{r}
######## 117 post #######

# 3368, 3718 with later dates should be moved to delayed

## sort by 'id' and 'start_date' in ascending order
df_Post117 <- df_Post117 %>%
  arrange(id, start_date)

## remove duplicate 'id's, keeping the first occurrence
df_Post117 <- df_Post117 %>%
  filter(!duplicated(id))

## separate the removed rows (later dates)
rows_to_move <- df_Post117 %>%
  filter(duplicated(id, fromLast = TRUE))

## append the later rows to 'df_Delayed117'
df_Delayed117 <- bind_rows(df_Delayed117, rows_to_move)


# check duplicated rows again
dupRows_Post117 <- df_Post117 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()
print(dupRows_Post117)
```

clean dup rows delayed 117
```{r}
######## 117 delayed #######
# 3411 Samantha should be removed
df_Delayed117 = df_Delayed117 %>% filter(!(id==3411 & ra == "Samantha"))

# 3411  with earlier dates should be moved to df_Post117
row_to_move <- df_Delayed117 %>%
  filter(id == 3411) %>%
  slice_min(order_by = start_date)

## Step 2: Remove this row from df_Delayed117
df_Delayed117 <- df_Delayed117 %>%
  filter(!(id == 3411 & start_date == row_to_move$start_date))

## Step 3: Append the identified row to df_Post117
df_Post117 <- bind_rows(df_Post117, row_to_move)


# 3425 KH should be 3426
df_Delayed117 = df_Delayed117 %>% 
  mutate(id = if_else(id == 3425 & ra == "KH", 3426, id))

# 3430 and 3278 with earlier dates should be removed (RA already re-entered it to df_Post107)
## Identify the rows with ids 3430 and 3278 with the earliest dates
rows_to_move <- df_Delayed117 %>%
  filter(id %in% c(3430, 3278)) %>%
  group_by(id) %>%
  slice_min(order_by = start_date) %>%
  ungroup()

# remove these rows from df_Delayed117
df_Delayed117 <- df_Delayed117 %>%
  anti_join(rows_to_move, by = c("id", "start_date"))

# check duplicated rows again
dupRows_Delayed117 <- df_Delayed117 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()


print(dupRows_Delayed117)
```

### Score 117
Full score for non CR: 26 points
```{r}
# create a function
Score117Func = function(df) {
  
  # q1, 2 points
  df$q1_init_score = ifelse(grepl("soccer", tolower(df$q1_init_choice)) | 
                             grepl("soccer", tolower(df$q1_init_text)), 2, 0)
  
  df$q1_rpt_score = ifelse(grepl("soccer", tolower(df$q1_rpt_choice)) | 
                             grepl("soccer", tolower(df$q1_rpt_text)), 1, 0)
  
  # q2, 2 points
  df$q2_init_score = ifelse(grepl("great things", tolower(df$q2_init_choice)) | 
                             grepl("great things", tolower(df$q2_init_text)), 2, 0)
  
  df$q2_rpt_score = ifelse(grepl("great things", tolower(df$q2_rpt_choice)) | 
                             grepl("great things", tolower(df$q2_rpt_text)), 1, 0)
  
  # q3, 2 points
  df$q3_init_score = ifelse(grepl("tight|small", tolower(df$q3_init_choice)) | 
                             grepl("tight|small", tolower(df$q3_init_text)), 2, 0)
  
  df$q3_rpt_score = ifelse(grepl("tight|small", tolower(df$q3_rpt_choice)) | 
                             grepl("tight|small", tolower(df$q3_rpt_text)), 1, 0)
  
  # q4-cr-no-scpre
  
  # q5, 2 points (a+b)
  df$q5a_init_score = ifelse(grepl("b", tolower(df$q5a_init_choice)) | 
                             grepl("b", tolower(df$q5a_init_text)), 1, 0)
  
  df$q5b_init_score = ifelse(grepl("d", tolower(df$q5b_init_choice)) | 
                             grepl("d", tolower(df$q5b_init_text)), 1, 0)
  
  # q6, 2 points
  df$q6_init_score = ifelse(grepl("tongue", tolower(df$q6_init_choice)) | 
                             grepl("tongue", tolower(df$q6_init_text)), 2, 0)
  
  df$q6_rpt_score = ifelse(grepl("tongue", tolower(df$q6_rpt_choice)) | 
                             grepl("tongue", tolower(df$q6_rpt_text)), 1, 0)
  
  # q7, 2 points
  df$q7_init_score = ifelse(grepl("smell", tolower(df$q7_init_choice)) | 
                             grepl("smell", tolower(df$q7_init_text)), 2, 0)
  
  df$q7_rpt_score = ifelse(grepl("smell", tolower(df$q7_rpt_choice)) | 
                             grepl("smell", tolower(df$q7_rpt_text)), 1, 0)
  
  # q8, 2 points
  df$q8_init_score = ifelse(grepl("miss", tolower(df$q8_init_choice)) | 
                             grepl("miss", tolower(df$q8_init_text)), 2, 0)
  
  df$q8_rpt_score = ifelse(grepl("miss", tolower(df$q8_rpt_choice)) | 
                             grepl("miss", tolower(df$q8_rpt_text)), 1, 0)
  
 # q9, 2 points
  df$q9_init_score = ifelse(grepl("molt", tolower(df$q9_init_choice)) | 
                           grepl("molt", tolower(df$q9_init_text)), 2, 0)

  df$q9_rpt_score = ifelse(grepl("molt", tolower(df$q9_rpt_choice)) | 
                          grepl("molt", tolower(df$q9_rpt_text)), 1, 0)

  # q10, 2 points
  df$q10_init_score = ifelse(grepl("magnifying", tolower(df$q10_init_choice)) | 
                            grepl("magnifying", tolower(df$q10_init_text)), 2, 0)

  df$q10_rpt_score = ifelse(grepl("magnifying", tolower(df$q10_rpt_choice)) | 
                           grepl("magnifying", tolower(df$q10_rpt_text)), 1, 0)

  # q11, 2 points
  df$q11_init_score = ifelse(grepl("molt", tolower(df$q11_init_choice)) | 
                              grepl("molt", tolower(df$q11_init_text)), 2, 0)
  
  df$q11_rpt_score = ifelse(grepl("molt", tolower(df$q11_rpt_choice)) | 
                             grepl("molt", tolower(df$q11_rpt_text)), 1, 0)
  
  # q12, 2 points
  df$q12_init_score = ifelse(grepl("molt", tolower(df$q12_init_choice)) | 
                              grepl("molt", tolower(df$q12_init_text)), 2, 0)
  
  df$q12_rpt_score = ifelse(grepl("molt", tolower(df$q12_rpt_choice)) | 
                             grepl("molt", tolower(df$q12_rpt_text)), 1, 0)
  
  # q13, 2 points
  df$q13_init_score = ifelse(grepl("grow", tolower(df$q13_init_choice)) | 
                              grepl("grow", tolower(df$q13_init_text)), 2, 0)
  
  df$q13_rpt_score = ifelse(grepl("grow", tolower(df$q13_rpt_choice)) | 
                             grepl("grow", tolower(df$q13_rpt_text)), 1, 0)
  
  # q14, 2 points
  df$q14_init_score = ifelse(grepl("forest|wood|jungle|grass", tolower(df$q14_init_choice)) | 
                              grepl("forest|wood|jungle|grass", tolower(df$q14_init_text)), 2, 0)
  
  df$q14_rpt_score = ifelse(grepl("forest|wood|jungle|grass", tolower(df$q14_rpt_choice)) | 
                             grepl("forest|wood|jungle|grass", tolower(df$q14_rpt_text)), 1, 0)
  
  # q15, cr, no score
  
  # initial and reprompt total scores
  df$init_total_score = rowSums(df %>% dplyr::select(contains("init_score")), na.rm = TRUE)
  df$rpt_total_score = rowSums(df %>% dplyr::select(contains("rpt_score")), na.rm = TRUE)
  df$total_score = df$init_total_score + df$rpt_total_score
  
  return(df)
}

# apply to post and delayed 117
df_Post117 = Score117Func(df_Post117)
df_Delayed117 = Score117Func(df_Delayed117)
```

Rename for post and delayed 117
```{r}
# Post 117
colnames(df_Post117)[-1] = paste0("p117_", colnames(df_Post117)[-1])

# Delayed 117
colnames(df_Delayed117)[-1] = paste0("d117_", colnames(df_Delayed117)[-1])
```

## Episode 109 post and delayed
Rename 109
```{r}
# print(colnames(df_Post109))

# set up column names for 109
colNames109 = c("id", "ra", "start_date", "q1_init_choice", "q1_init_text", "q1_rpt_choice", "q1_rpt_text",
"q2_init_choice", "q2_init_text", "q2_rpt_choice", "q2_rpt_text",
"q3_init_choice", "q3_init_text", "q3_rpt_choice", "q3_rpt_text",
"q4a_init_choice", "q4a_init_text",
"q4b_cr", "q4c_cr", "q4d_cr",
"q5a_init_choice", "q5a_init_text",
"q5b_cr",
"q6a_init_choice", "q6a_init_text",
"q6b_cr",
"q7a_init_choice", "q7a_init_text",
"q7b_cr",
"q8_init_choice", "q8_init_text", "q8_rpt_choice", "q8_rpt_text",
"q9_init_choice", "q9_init_text", "q9_rpt_choice", "q9_rpt_text",
"q10a_cr", "q10b_cr",
"q11a_cr", "q11b_cr", "q11c_cr",
"notes")

# rename
colnames(df_Post109) = colNames109
colnames(df_Delayed109) = colNames109

# convert id to be numeric
df_Delayed109$id = as.numeric(df_Delayed109$id)
df_Post109$id = as.numeric(df_Post109$id)
```

### Check duplicated rows
```{r}
dupRows_Post109 <- df_Post109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post109)

dupRows_Delayed109 <- df_Delayed109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()


print(dupRows_Delayed109)
```
Clean dup rows post 109
```{r}
# 3425 KH should be 3426
df_Post109 = df_Post109 %>% 
  mutate(id = if_else(id == 3425 & ra == "KH", 3426, id))

# 3437 and 3278 with later dates should be moved to df_Delayed109
## sort by 'id' and 'start_date' in ascending order
df_Post109 <- df_Post109 %>%
  arrange(id, start_date)

## remove duplicate 'id's, keeping the first occurrence
df_Post109 <- df_Post109 %>%
  filter(!duplicated(id))

## separate the removed rows (later dates)
rows_to_move <- df_Post109 %>%
  filter(duplicated(id, fromLast = TRUE))

## append the later rows to 'df_Delayed117'
df_Delayed109 <- bind_rows(df_Delayed109, rows_to_move)

# check dup rows again
dupRows_Post109 <- df_Post109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post109)
```

### Score 109
Full score for non CR: 14 points
```{r}
# create a function
Score109Func = function(df) {
  
  # q1, 2 points
  df$q1_init_score = ifelse(grepl("car", tolower(df$q1_init_choice)) | 
                             grepl("car", tolower(df$q1_init_text)), 2, 0)
  
  df$q1_rpt_score = ifelse(grepl("car", tolower(df$q1_rpt_choice)) | 
                             grepl("car", tolower(df$q1_rpt_text)), 1, 0)
  
  # q2, 2 points
  df$q2_init_score = ifelse(grepl("slow", tolower(df$q2_init_choice)) | 
                             grepl("slow", tolower(df$q2_init_text)), 2, 0)
  
  df$q2_rpt_score = ifelse(grepl("slow", tolower(df$q2_rpt_choice)) | 
                             grepl("slow", tolower(df$q2_rpt_text)), 1, 0)
  
  # q3, 2 points
  df$q3_init_score = ifelse(grepl("point|streamline", tolower(df$q3_init_choice)) | 
                             grepl("point|streamline", tolower(df$q3_init_text)), 2, 0)
  
  df$q3_rpt_score = ifelse(grepl("point|streamline", tolower(df$q3_rpt_choice)) | 
                             grepl("point|streamline", tolower(df$q3_rpt_text)), 1, 0)
  
  # q4a, initial only, 1 point
  df$q4a_init_score = ifelse(
    grepl("paint", tolower(df$q4a_init_choice)) & 
    grepl("cupholder", tolower(df$q4a_init_choice)) & 
    grepl("shape", tolower(df$q4a_init_choice)) |
    grepl("paint", tolower(df$q4a_init_text)) & 
    grepl("cupholder", tolower(df$q4a_init_text)) & 
    grepl("shape", tolower(df$q4a_init_text)),
  1, 0)
  
  # q4b, q4c, q4d, cr, no score
  
  # q5a, initial only, 1 point
  df$q5a_init_score = ifelse(grepl("a", tolower(df$q5a_init_choice)) | 
                             grepl("a", tolower(df$q5a_init_text)), 1, 0)
  
  # q5b, cr, no score
  
  # q6a, initial only, 1 point
  df$q6a_init_score = ifelse(grepl("a", tolower(df$q6a_init_choice)) | 
                             grepl("a", tolower(df$q6a_init_text)), 1, 0)
  
  # q6b, cr, no score
  
  # q7a, initial only, 1 point
  df$q7a_init_score = ifelse(grepl("c", tolower(df$q7a_init_choice)) | 
                             grepl("c", tolower(df$q7a_init_text)), 1, 0)
  
  # q7b, cr, no score
  
  # q8, 2 points
  df$q8_init_score = ifelse(grepl("fast", tolower(df$q8_init_choice)) | 
                             grepl("fast", tolower(df$q8_init_text)), 2, 0)
  
  df$q8_rpt_score = ifelse(grepl("fast", tolower(df$q8_rpt_choice)) | 
                             grepl("fast", tolower(df$q8_rpt_text)), 1, 0)
  
 # q9, 2 points
  df$q9_init_score = ifelse(grepl("pushed back", tolower(df$q9_init_choice)) | 
                           grepl("pushed back", tolower(df$q9_init_text)), 2, 0)

  df$q9_rpt_score = ifelse(grepl("pushed back", tolower(df$q9_rpt_choice)) | 
                          grepl("pushed back", tolower(df$q9_rpt_text)), 1, 0)
  
  # q10, cr, no score
  
  # q11, cr, no score
  
  # initial and reprompt total scores
  df$init_total_score = rowSums(df %>% dplyr::select(contains("init_score")), na.rm = TRUE)
  df$rpt_total_score = rowSums(df %>% dplyr::select(contains("rpt_score")), na.rm = TRUE)
  df$total_score = df$init_total_score + df$rpt_total_score
  
  return(df)
}

# apply to post and delayed 109
df_Post109 = Score109Func(df_Post109)
df_Delayed109 = Score109Func(df_Delayed109)
```

Rename for post and delayed 109
```{r}
# Post 109
colnames(df_Post109)[-1] = paste0("p109_", colnames(df_Post109)[-1])

# Delayed 109
colnames(df_Delayed109)[-1] = paste0("d109_", colnames(df_Delayed109)[-1])
```

## Episode 101 post
```{r}
# print(colnames(df_Post101))

# set up column names for 101
colNames101 = c("id", "ra" , "start_date",
                "q1_init_choice", "q1_init_text", "q1_rpt_choice", "q1_rpt_text",
                "q2_init_choice", "q2_init_text", "q2_rpt_choice", "q2_rpt_text",
                "q3_init_choice", "q3_init_text", "q3_rpt_choice", "q3_rpt_text",
                "q4_init_choice", "q4_init_text", "q4_rpt_choice", "q4_rpt_text",
                "q5_init_choice", "q5_init_text", "q5_rpt_choice", "q5_rpt_text",
                "q6_init_choice", "q6_init_text", "q6_rpt_choice", "q6_rpt_text",
                "q7_init_choice", "q7_init_text", "q7_rpt_choice", "q7_rpt_text",
                "q8_init_choice", "q8_init_text", "q8_rpt_choice", "q8_rpt_text",
                "q9a_init_choice", "q9a_init_text", "q9b_init_choice", "q9b_init_text",
                "q10_init_choice", "q10_init_text", "q10_rpt_choice", "q10_rpt_text",
                "q11_init_choice", "q11_init_text", "q11_rpt_choice", "q11_rpt_text",
                
                # vocab
                "q12a_cr", "q12b_init_choice", 
                "q13a_init_choice", "q13b_init_choice", "q13c_init_choice", "q13d_init_choice",
                "q14a_init_choice", "q14b_init_choice", "q14c_init_choice", 
                "notes")

# rename
colnames(df_Post101) = colNames101
# convert id to be numeric
df_Post101$id = as.numeric(df_Post101$id)
```

### Check dup rows post 101
```{r}
dupRows_Post101 <- df_Post101 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post101)

```
```{r}
# 3399, 3398, 3396 have dups and both rows should be removed
df_Post101 = df_Post101 %>% filter(id!=3399 & id!=3398 & id!=3396)

# 3289 and 3681 with earlier time should be removed
## Identify the rows with ids 3430 and 3278 with the earliest dates
rows_to_move <- df_Post101 %>%
  filter(id %in% c(3289, 3681)) %>%
  group_by(id) %>%
  slice_min(order_by = start_date) %>%
  ungroup()

# remove these rows from df_Post101
df_Post101 <- df_Post101 %>%
  anti_join(rows_to_move, by = c("id", "start_date"))


# check duplicated rows again
dupRows_Post101 <- df_Post101 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post101)
```


### Score 101
- Full score for non CR items: 22 points
- Full score for vocab items: 8 points
```{r}
# create a function
Score101Func = function(df) {
  
  # convert empty string to NA
  df[df==""]<-NA
  
  # q1, 2 points
  df$q1_init_score = ifelse(grepl("nectar", tolower(df$q1_init_choice)) | 
                             grepl("nectar", tolower(df$q1_init_text)), 2, 0)
  
  df$q1_rpt_score = ifelse(grepl("nectar", tolower(df$q1_rpt_choice)) | 
                             grepl("nectar", tolower(df$q1_rpt_text)), 1, 0)
  
  # q2, 2 points
  df$q2_init_score = ifelse(grepl("water", tolower(df$q2_init_choice)) | 
                             grepl("water", tolower(df$q2_init_text)), 2, 0)
  
  df$q2_rpt_score = ifelse(grepl("water", tolower(df$q2_rpt_choice)) | 
                             grepl("water", tolower(df$q2_rpt_text)), 1, 0)
  
  # q3, 2 points
  df$q3_init_score = ifelse(grepl("wing", tolower(df$q3_init_choice)) &
                              grepl("flap", tolower(df$q3_init_choice)) | 
                              grepl("wing", tolower(df$q3_init_text)) &
                              grepl("flap", tolower(df$q3_init_text)), 2, 0)
  
  df$q3_rpt_score = ifelse(grepl("wing", tolower(df$q3_rpt_choice)) &
                              grepl("flap", tolower(df$q3_rpt_choice)) | 
                              grepl("wing", tolower(df$q3_rpt_text)) &
                              grepl("flap", tolower(df$q3_rpt_text)), 1, 0)
  
  # q4, 2 points
  df$q4_init_score = ifelse(grepl("thick|sticky|gooey|slimy", tolower(df$q4_init_choice)) | 
                             grepl("thick|sticky|gooey|slimy", tolower(df$q4_init_text)), 2, 0)
  
  df$q4_rpt_score = ifelse(grepl("thick|sticky|gooey|slimy", tolower(df$q4_rpt_choice)) | 
                             grepl("thick|sticky|gooey|slimy", tolower(df$q4_rpt_text)), 1, 0)
  
  # q5, 2 points
  df$q5_init_score = ifelse(grepl("ketchup", tolower(df$q5_init_choice)) | 
                             grepl("ketchup", tolower(df$q5_init_text)), 2, 0)

  df$q5_rpt_score = ifelse(grepl("ketchup", tolower(df$q5_rpt_choice)) | 
                             grepl("ketchup", tolower(df$q5_rpt_text)), 1, 0)
  
  # q6, 2 points
  df$q6_init_score = ifelse(grepl("ketchup", tolower(df$q6_init_choice)) & 
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q6_init_choice)) | 
                             grepl("ketchup", tolower(df$q6_init_text)) &
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q6_init_text)), 2, 0)
  
  df$q6_rpt_score = ifelse(grepl("ketchup", tolower(df$q6_rpt_choice)) & 
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q6_rpt_choice)) | 
                             grepl("ketchup", tolower(df$q6_rpt_text)) &
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q6_rpt_text)), 1, 0)
  
  # q7, 2 points
  df$q7_init_score = ifelse(grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q7_init_choice)) | 
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q7_init_text)), 2, 0)
  
  df$q7_rpt_score = ifelse(grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q7_rpt_choice)) | 
                             grepl("thick|sticky|gooey|goopy|slimy", tolower(df$q7_rpt_text)), 1, 0)
  
  # q8, 2 points
  df$q8_init_score = ifelse(grepl("honey", tolower(df$q8_init_choice)) | 
                             grepl("honey", tolower(df$q8_init_text)), 2, 0)
  
  df$q8_rpt_score = ifelse(grepl("honey", tolower(df$q8_rpt_choice)) | 
                             grepl("honey", tolower(df$q8_rpt_text)), 1, 0)
  
 # q9, 2 points (a+b)
  df$q9a_init_score = ifelse(grepl("a", tolower(df$q9a_init_choice)) | 
                           grepl("a", tolower(df$q9a_init_text)), 1, 0)

  df$q9b_init_score = ifelse(grepl("b", tolower(df$q9b_init_choice)) | 
                           grepl("b", tolower(df$q9b_init_text)), 1, 0)

  # q10, 2 points
  df$q10_init_score = ifelse(grepl("add|put|with", tolower(df$q10_init_choice)) &
                              grepl("water", tolower(df$q10_init_choice)) | 
                             grepl("add|put|with", tolower(df$q10_init_text)) &
                              grepl("water", tolower(df$q10_init_text)), 2, 0)

  df$q10_rpt_score = ifelse(grepl("add|put|with", tolower(df$q10_rpt_choice)) &
                              grepl("water", tolower(df$q10_rpt_choice)) | 
                             grepl("add|put|with", tolower(df$q10_rpt_text)) &
                              grepl("water", tolower(df$q10_rpt_text)), 1, 0)

  # q11, 2 points
  df$q11_init_score = ifelse(grepl("add|put|with", tolower(df$q11_init_choice)) &
                              grepl("water", tolower(df$q11_init_choice)) | 
                             grepl("add|put|with", tolower(df$q11_init_text)) &
                              grepl("water", tolower(df$q11_init_text)), 2, 0)

  df$q11_rpt_score = ifelse(grepl("add|put|with", tolower(df$q11_rpt_choice)) &
                              grepl("water", tolower(df$q11_rpt_choice)) | 
                             grepl("add|put|with", tolower(df$q11_rpt_text)) &
                              grepl("water", tolower(df$q11_rpt_text)), 1, 0)
  
  ### vocab items
  ## q12a, cr, no score

  # q12b, 1 point
  df$q12b_score_vocab <- ifelse(is.na(df$q12b_init_choice), NA, 
                                ifelse(grepl("c", tolower(df$q12b_init_choice)), 1, 0))
  
  # q13a, 1 point
  df$q13a_score_vocab <- ifelse(is.na(df$q13a_init_choice), NA, 
                                ifelse(grepl("yes", tolower(df$q13a_init_choice)), 1, 0))
  
  # q13b, 1 point
  df$q13b_score_vocab <- ifelse(is.na(df$q13b_init_choice), NA, 
                                ifelse(grepl("\\bno\\b", tolower(df$q13b_init_choice)), 1, 0))
  
  # q13c, 1 point
  df$q13c_score_vocab <- ifelse(is.na(df$q13c_init_choice), NA, 
                                ifelse(grepl("yes", tolower(df$q13c_init_choice)), 1, 0))
  
  # q13d, 1 point
  df$q13d_score_vocab <- ifelse(is.na(df$q13d_init_choice), NA, 
                                ifelse(grepl("\\bno\\b", tolower(df$q13d_init_choice)), 1, 0))
  
  # q14a, 1 point
  df$q14a_score_vocab <- ifelse(is.na(df$q14a_init_choice), NA, 
                                ifelse(grepl("\\bno\\b", tolower(df$q14a_init_choice)), 1, 0))
  
  # q14b, 1 point
  df$q14b_score_vocab <- ifelse(is.na(df$q14b_init_choice), NA, 
                                ifelse(grepl("yes", tolower(df$q14b_init_choice)), 1, 0))
  
  # q14c, 1 point
  df$q14c_score_vocab <- ifelse(is.na(df$q14c_init_choice), NA, 
                                ifelse(grepl("\\bno\\b", tolower(df$q14c_init_choice)), 1, 0))

  
  # initial and reprompt total scores
  df$init_total_score = rowSums(df %>% dplyr::select(contains("init_score")), na.rm = TRUE)
  df$rpt_total_score = rowSums(df %>% dplyr::select(contains("rpt_score")), na.rm = TRUE)
  df$vocab_total_score = rowSums(df %>% dplyr::select(contains("score_vocab")), na.rm = F)
  df$total_score = df$init_total_score + df$rpt_total_score
  
  # convert children not receiving vocab items to NA
  
  
  return(df)
}

# apply to post 101
df_Post101 = Score101Func(df_Post101)
```

Rename for post101
```{r}
# Post 101
colnames(df_Post101)[-1] = paste0("p101_", colnames(df_Post101)[-1])
```


## Write csv
```{r}
# csv
write.csv(df_Tracker, "clean_data/tracker.csv")
write.csv(df_Post117, "clean_data/post_117.csv")
write.csv(df_Delayed117, "clean_data/delayed_117.csv")

write.csv(df_Post109, "clean_data/post_109.csv")
write.csv(df_Delayed109, "clean_data/delayed_109.csv")

write.csv(df_Post101, "clean_data/post_101.csv")

# excel
write.xlsx(df_Post117, "clean_data/post_117.xlsx")
write.xlsx(df_Delayed117, "clean_data/delayed_117.xlsx")

write.xlsx(df_Post109, "clean_data/post_109.xlsx")
write.xlsx(df_Delayed109, "clean_data/delayed_109.xlsx")

write.xlsx(df_Post101, "clean_data/post_101.xlsx")
```

# 4. Merge scores to tracker
```{r}
df_Master = merge(df_Tracker, df_Post117, by=c("id"), all.x=T)
df_Master = merge(df_Master, df_Delayed117, by=c("id"), all.x=T)
df_Master = merge(df_Master, df_Post109, by=c("id"), all.x=T)
df_Master = merge(df_Master, df_Delayed109, by=c("id"), all.x=T)
df_Master = merge(df_Master, df_Post101, by=c("id"), all.x=T)
```

```{r}
# check duplicated rows again
dupRows <- df_Master %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows)
```

```{r}
# rename CA to be group
df_Master = df_Master %>% rename(group =CA)

# generate final total score
df_Master$agg_post_score = df_Master$p117_total_score + df_Master$p109_total_score + df_Master$p101_total_score
df_Master$agg_delayed_score = df_Master$d117_total_score + df_Master$d109_total_score

# write
 write.csv(df_Master, "clean_data/master.csv")
```


