---
title: "Scoring immediate post-test for ep 101"
author: "Kunlei He"
date: "2024-10-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries
```{r}
library(dplyr)
```

# Load Data
```{r}
# Raw score downloaded from Qualtrics
df_RawPost101 <- read.csv("raw_data/raw_post_101.csv")

# Tracker
df_Tracker <- read.csv("clean_data/tracker.csv")
```

# Data Cleaning
## Clean columns and ids
```{r}
# remove unuseful columns
df_Post101 = df_RawPost101[, -c(2:17)]

# remove first two rows
df_Post101 = df_Post101[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Post101$id = ifelse(df_Post101$Intro_4 %in% c(3000:4000), df_Post101$Intro_4, df_Post101$Intro_5)
# get the ra initials
df_Post101$ra = ifelse(is.na(as.numeric(as.character(df_Post101$Intro_4))), df_Post101$Intro_4, df_Post101$Intro_5)
# get rid of intro_4 and intro_5
df_Post101 = df_Post101 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Post101 = df_Post101 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Post101 = df_Post101 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post101$id that are NOT present in df_Tracker$id
diffID = df_Post101$id[!df_Post101$id %in% df_Tracker$id]
print(diffID) # check with Kelsy - These are pre shutdown ids
```

## Rename columns
```{r}
colNames101 = c("id", "ra" , "start_date",
                "q1_drink_init_choice", "q1_drink_init_text", "q1_drink_rpt_choice", "q1_drink_rpt_text",
                "q2_nectar_init_choice", "q2_nectar_init_text", "q2_nectar_rpt_choice", "q2_nectar_rpt_text",
                "q3_wings_init_choice", "q3_wings_init_text", "q3_wings_rpt_choice", "q3_wings_rpt_text",
                "q4_goopy_init_choice", "q4_goopy_init_text", "q4_goopy_rpt_choice", "q4_goopy_rpt_text",
                "q5_wait_init_choice", "q5_wait_init_text", "q5_wait_rpt_choice", "q5_wait_rpt_text",
                "q6_line_init_choice", "q6_line_init_text", "q6_line_rpt_choice", "q6_line_rpt_text",
                "q7_out_init_choice", "q7_out_init_text", "q7_out_rpt_choice", "q7_out_rpt_text",
                "q8_jar_init_choice", "q8_jar_init_text", "q8_jar_rpt_choice", "q8_jar_rpt_text",
                "q9a_goopier_init_choice", "q9a_goopier_init_text", "q9b_runnier_init_choice", "q9b_runnier_init_text",
                "q10_add_init_choice", "q10_add_init_text", "q10_add_rpt_choice", "q10_add_rpt_text",
                "q11_next_init_choice", "q11_next_init_text", "q11_next_rpt_choice", "q11_next_rpt_text",
                
                # vocab
                "q12a_vocab_cr", "q12b_vocab_init_choice", 
                "q13a_vocab_init_choice", "q13b_vocab_init_choice", "q13c_vocab_init_choice", "q13d_vocab_init_choice",
                "q14a_vocab_init_choice", "q14b_vocab_init_choice", "q14c_vocab_init_choice", 
                "notes")

# rename
colnames(df_Post101) = colNames101
# convert id to be numeric
df_Post101$id = as.numeric(df_Post101$id)
```

## Handle duplicated ids
```{r}
dupRows_Post101 <- df_Post101 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post101)
```

```{r}
# 3399, 3398, 3396 have dups and both rows should be removed
df_Post101 = df_Post101 %>% filter(id!=3399 & id!=3398 & id!=3396)

# 3289 and 3681 with earlier time should be removed
## Identify the rows with ids 3430 and 3278 with the earliest dates
rows_to_move <- df_Post101 %>%
  filter(id %in% c(3289, 3681)) %>%
  group_by(id) %>%
  slice_min(order_by = start_date) %>%
  ungroup()

# remove these rows from df_Post101
df_Post101 <- df_Post101 %>%
  anti_join(rows_to_move, by = c("id", "start_date"))


# check duplicated rows again
dupRows_Post101 <- df_Post101 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post101)
```

# Scoring
- Full score for episode 101 items is 22 (no constructive items, not including vocabulary items)
- Full score for vocabulary items is 8 points

## Individual items
### Content
#### q1_drink
```{r}
Func_q1_drink_score <- function(df) {
  df$q1_drink_init_score = ifelse(grepl("nectar", df$q1_drink_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("nectar", df$q1_drink_init_text, ignore.case = TRUE), 2, 0))

  df$q1_drink_rpt_score = ifelse(grepl("nectar", df$q1_drink_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("nectar", df$q1_drink_rpt_text, ignore.case = TRUE), 1, 0))

  df$q1_drink_rpt_score = ifelse(df$q1_drink_init_score == 2, 0, df$q1_drink_rpt_score)
  
  df$q1_drink_score = df$q1_drink_init_score + df$q1_drink_rpt_score
  
  print(paste("The range of q1_drink_score is:", 
              min(df$q1_drink_score, na.rm = TRUE), "to", 
              max(df$q1_drink_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q1_drink_score(df_Post101)
```

#### q2_nectar
```{r}
Func_q2_nectar_score <- function(df) {
  df$q2_nectar_init_score = ifelse(grepl("water", df$q2_nectar_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("water", df$q2_nectar_init_text, ignore.case = TRUE), 2, 0))

  df$q2_nectar_rpt_score = ifelse(grepl("water", df$q2_nectar_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("water", df$q2_nectar_rpt_text, ignore.case = TRUE), 1, 0))

  df$q2_nectar_rpt_score = ifelse(df$q2_nectar_init_score == 2, 0, df$q2_nectar_rpt_score)
  
  df$q2_nectar_score = df$q2_nectar_init_score + df$q2_nectar_rpt_score
  
  print(paste("The range of q2_nectar_score is:", 
              min(df$q2_nectar_score, na.rm = TRUE), "to", 
              max(df$q2_nectar_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q2_nectar_score(df_Post101)
```

#### q3_wings
```{r}
Func_q3_wings_score <- function(df) {
  df$q3_wings_init_score = ifelse((grepl("wing", df$q3_wings_init_choice, ignore.case = TRUE) & grepl("use|flap", df$q3_wings_init_choice, ignore.case = TRUE)) | 
                                 (grepl("wing", df$q3_wings_init_text, ignore.case = TRUE) & grepl("use|flap", df$q3_wings_init_text, ignore.case = TRUE)), 2, 0)

  df$q3_wings_rpt_score = ifelse((grepl("wing", df$q3_wings_rpt_choice, ignore.case = TRUE) & grepl("use|flap", df$q3_wings_rpt_choice, ignore.case = TRUE)) | 
                                 (grepl("wing", df$q3_wings_rpt_text, ignore.case = TRUE) & grepl("use|flap", df$q3_wings_rpt_text, ignore.case = TRUE)), 1, 0)


  df$q3_wings_rpt_score = ifelse(df$q3_wings_init_score == 2, 0, df$q3_wings_rpt_score)
  
  df$q3_wings_score = df$q3_wings_init_score + df$q3_wings_rpt_score
  
  print(paste("The range of q3_wings_score is:", 
              min(df$q3_wings_score, na.rm = TRUE), "to", 
              max(df$q3_wings_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q3_wings_score(df_Post101)
```

#### q4_goopy
```{r}
Func_q4_goopy_score <- function(df) {
  df$q4_goopy_init_score = ifelse(grepl("thick|sticky|slimy|gooey", df$q4_goopy_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("thick|sticky|slimy|gooey", df$q4_goopy_init_text, ignore.case = TRUE), 2, 0))

  df$q4_goopy_rpt_score = ifelse(grepl("thick|sticky|slimy|gooey", df$q4_goopy_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("thick|sticky|slimy|gooey", df$q4_goopy_rpt_text, ignore.case = TRUE), 1, 0))

  df$q4_goopy_rpt_score = ifelse(df$q4_goopy_init_score == 2, 0, df$q4_goopy_rpt_score)
  
  df$q4_goopy_score = df$q4_goopy_init_score + df$q4_goopy_rpt_score
  
  print(paste("The range of q4_goopy_score is:", 
              min(df$q4_goopy_score, na.rm = TRUE), "to", 
              max(df$q4_goopy_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q4_goopy_score(df_Post101)
```

#### q5_wait
```{r}
Func_q5_wait_score <- function(df) {
  df$q5_wait_init_score = ifelse(grepl("ketchup", df$q5_wait_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("ketchup", df$q5_wait_init_text, ignore.case = TRUE), 2, 0))

  df$q5_wait_rpt_score = ifelse(grepl("ketchup", df$q5_wait_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("ketchup", df$q5_wait_rpt_text, ignore.case = TRUE), 1, 0))

  df$q5_wait_rpt_score = ifelse(df$q5_wait_init_score == 2, 0, df$q5_wait_rpt_score)
  
  df$q5_wait_score = df$q5_wait_init_score + df$q5_wait_rpt_score
  
  print(paste("The range of q5_wait_score is:", 
              min(df$q5_wait_score, na.rm = TRUE), "to", 
              max(df$q5_wait_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q5_wait_score(df_Post101)
```

#### q6_line
```{r}
Func_q6_line_score <- function(df) {
  texture_patterns <- "thick|sticky|slimy|gooey"
  not_out_patterns <- "not.*out|n['’]t.*out"
  
   df$q6_line_init_score = ifelse((grepl("ketchup", df$q6_line_init_choice, ignore.case = TRUE) & grepl(paste0(texture_patterns, "|", not_out_patterns), df$q6_line_init_choice, ignore.case = TRUE)) | 
                                 (grepl("ketchup", df$q6_line_init_text, ignore.case = TRUE) & grepl(paste0(texture_patterns, "|", not_out_patterns), df$q6_line_init_text, ignore.case = TRUE)), 
                                 2, 0)

  df$q6_line_rpt_score = ifelse((grepl("ketchup", df$q6_line_rpt_choice, ignore.case = TRUE) & grepl(paste0(texture_patterns, "|", not_out_patterns), df$q6_line_rpt_choice, ignore.case = TRUE)) | 
                                 (grepl("ketchup", df$q6_line_rpt_text, ignore.case = TRUE) & grepl(paste0(texture_patterns, "|", not_out_patterns), df$q6_line_rpt_text, ignore.case = TRUE)), 
                                 1, 0)

  # Condition to set repeat score to 0 if initial score is 2
  df$q6_line_rpt_score = ifelse(df$q6_line_init_score == 2, 0, df$q6_line_rpt_score)
  
  # Combine initial and repeat scores
  df$q6_line_score = df$q6_line_init_score + df$q6_line_rpt_score
  
  # Print the range of scores
  print(paste("The range of q6_line_score is:", 
              min(df$q6_line_score, na.rm = TRUE), "to", 
              max(df$q6_line_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q6_line_score(df_Post101)
```
#### q7_out
```{r}
Func_q7_out_score <- function(df) {
  df$q7_out_init_score = ifelse(grepl("thick|sticky|slimy|gooey", df$q7_out_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("thick|sticky|slimy|gooey", df$q7_out_init_text, ignore.case = TRUE), 2, 0))

  df$q7_out_rpt_score = ifelse(grepl("thick|sticky|slimy|gooey", df$q7_out_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("thick|sticky|slimy|gooey", df$q7_out_rpt_text, ignore.case = TRUE), 1, 0))

  df$q7_out_rpt_score = ifelse(df$q7_out_init_score == 2, 0, df$q7_out_rpt_score)
  
  df$q7_out_score = df$q7_out_init_score + df$q7_out_rpt_score
  
  print(paste("The range of q7_out_score is:", 
              min(df$q7_out_score, na.rm = TRUE), "to", 
              max(df$q7_out_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q7_out_score(df_Post101)
```
#### q8_jar
```{r}
Func_q8_jar_score <- function(df) {
  df$q8_jar_init_score = ifelse(grepl("honey", df$q8_jar_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("honey", df$q8_jar_init_text, ignore.case = TRUE), 2, 0))

  df$q8_jar_rpt_score = ifelse(grepl("honey", df$q8_jar_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("honey", df$q8_jar_rpt_text, ignore.case = TRUE), 1, 0))

  df$q8_jar_rpt_score = ifelse(df$q8_jar_init_score == 2, 0, df$q8_jar_rpt_score)
  
  df$q8_jar_score = df$q8_jar_init_score + df$q8_jar_rpt_score
  
  print(paste("The range of q8_jar_score is:", 
              min(df$q8_jar_score, na.rm = TRUE), "to", 
              max(df$q8_jar_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q8_jar_score(df_Post101)
```

#### q9_video
- consist of q9a_goopier and q9b_runnier
```{r}
Func_q9_video_score <- function(df) {
  df$q9a_goopier_init_score = ifelse(grepl("A", df$q9a_goopier_init_choice), 1,
                                         ifelse(grepl("A", df$q9a_goopier_init_text), 1, 0))

  df$q9b_runnier_init_score = ifelse(grepl("B", df$q9b_runnier_init_choice), 1,
                                         ifelse(grepl("B", df$q9b_runnier_init_text), 1, 0))

  df$q9_video_score = df$q9a_goopier_init_score + df$q9b_runnier_init_score
  
  print(paste("The range of q9_video_score is:", 
              min(df$q9_video_score, na.rm = TRUE), "to", 
              max(df$q9_video_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q9_video_score(df_Post101)
```

#### q10_add
```{r}
Func_q10_add_score <- function(df) {
  df$q10_add_init_score = ifelse((grepl("water", df$q10_add_init_choice, ignore.case = TRUE) & grepl("get|put|use|add", df$q10_add_init_choice, ignore.case = TRUE)) | 
                                 (grepl("water", df$q10_add_init_text, ignore.case = TRUE) & grepl("get|put|use|add", df$q10_add_init_text, ignore.case = TRUE)), 2, 0)

  df$q10_add_rpt_score = ifelse((grepl("water", df$q10_add_rpt_choice, ignore.case = TRUE) & grepl("get|put|use|add", df$q10_add_rpt_choice, ignore.case = TRUE)) | 
                                 (grepl("water", df$q10_add_rpt_text, ignore.case = TRUE) & grepl("get|put|use|add", df$q10_add_rpt_text, ignore.case = TRUE)), 1, 0)


  df$q10_add_rpt_score = ifelse(df$q10_add_init_score == 2, 0, df$q10_add_rpt_score)
  
  df$q10_add_score = df$q10_add_init_score + df$q10_add_rpt_score
  
  print(paste("The range of q10_add_score is:", 
              min(df$q10_add_score, na.rm = TRUE), "to", 
              max(df$q10_add_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q10_add_score(df_Post101)
```

#### q11_next
```{r}
Func_q11_next_score <- function(df) {
  df$q11_next_init_score = ifelse((grepl("water", df$q11_next_init_choice, ignore.case = TRUE) & grepl("more", df$q11_next_init_choice, ignore.case = TRUE)) | 
                                 (grepl("water", df$q11_next_init_text, ignore.case = TRUE) & grepl("more", df$q11_next_init_text, ignore.case = TRUE)), 2, 0)

  df$q11_next_rpt_score = ifelse((grepl("water", df$q11_next_rpt_choice, ignore.case = TRUE) & grepl("more", df$q11_next_rpt_choice, ignore.case = TRUE)) | 
                                 (grepl("water", df$q11_next_rpt_text, ignore.case = TRUE) & grepl("more", df$q11_next_rpt_text, ignore.case = TRUE)), 1, 0)


  df$q11_next_rpt_score = ifelse(df$q11_next_init_score == 2, 0, df$q11_next_rpt_score)
  
  df$q11_next_score = df$q11_next_init_score + df$q11_next_rpt_score
  
  print(paste("The range of q11_next_score is:", 
              min(df$q11_next_score, na.rm = TRUE), "to", 
              max(df$q11_next_score, na.rm = TRUE)))
  
  return (df)
}

df_Post101 <- Func_q11_next_score(df_Post101)
```

### Vocabulary PENDING
```{r}
Func_vocab_score <- function(df) {

  return (df)
}
```

## Aggregate scores PENDING
```{r}
# Aggregate all the columns that contain init_score to be free_recall_score
df_Post101$p101_init_total_score = rowSums(df_Post101[, grepl("init_score", colnames(df_Post101))], na.rm = TRUE)

# Aggregate all the columns that contain rpt_score to be reprompt_score
df_Post101$p101_rpt_total_score = rowSums(df_Post101[, grepl("rpt_score", colnames(df_Post101))], na.rm = TRUE)

# Aggregate all item score to be total_score
df_Post101$p101_total_score = rowSums(df_Post101[, c("q1_drink_score", "q2_nectar_score", "q3_wings_score", 
                                                "q4_goopy_score", "q5_wait_score", "q6_line_score", "q7_out_score", 
                                                "q8_jar_score", "q9_video_score", "q10_add_score", "q11_next_score")], na.rm = TRUE)

# Calculate recall and transfer score
## recall items: q1, q2, q3, q4, q5, q6, q10
## transfer items: q7, q8, q9, q11
df_Post101$p101_recall_score = rowSums(df_Post101[, c("q1_drink_score", "q2_nectar_score", "q3_wings_score", 
                                                "q4_goopy_score", "q5_wait_score", "q6_line_score", "q10_add_score")],
                               na.rm = TRUE)

df_Post101$p101_transfer_score = rowSums(df_Post101[, c("q7_out_score", "q8_jar_score", "q9_video_score", "q11_next_score")], 
                               na.rm = TRUE)

# Calculate narrative and science score
## narrative items: q3, q5
## science items: all remaining items
df_Post101$p101_narrative_score = rowSums(df_Post101[, c("q3_wings_score", "q5_wait_score")], na.rm = TRUE)
df_Post101$p101_science_score = rowSums(df_Post101[, c("q1_drink_score", "q2_nectar_score", "q4_goopy_score", 
                                                "q6_line_score", "q7_out_score", "q8_jar_score", 
                                                "q9_video_score", "q10_add_score", "q11_next_score")], na.rm = TRUE)

# Sanity check
df_Post101$p101_total_score_check = df_Post101$p101_init_total_score + df_Post101$p101_rpt_total_score

## check if there are rows where total_score and total_score_check are different
print(df_Post101 %>% filter(p101_total_score != p101_total_score_check))

## remove total_score_check column
df_Post101 <- df_Post101 %>% select(-p101_total_score_check)
```

# Write to file
```{r}
write.csv(df_Post101, "clean_data/post_101_scored.csv", row.names = FALSE)
```

# Psychometric Analysis
Metrics: 
- difficulty = (mean score / total score per item) * 100
  - problematic if less than 0.2 or greater than 0.8
- discrimination =  the correlation between the item score and the total score without that item for each child
  - problematic if less than 0.2
  
```{r}
# Load the data
# df_Post101 <- read.csv("clean_data/post_101_scored.csv")

# List of score columns
scoreCols <- c("q1_drink_score", "q2_nectar_score", "q3_wings_score", 
               "q4_goopy_score", "q5_wait_score", "q6_line_score", 
               "q7_out_score", "q8_jar_score", "q9_video_score", 
               "q10_add_score", "q11_next_score")

# Full score for all items
fullScore <- 2

# Calculate total score for discrimination (sum of all items per respondent)
totalScorePerChild <- rowSums(df_Post101[scoreCols], na.rm = TRUE)

# Create an empty dataframe to store the results with the same number of rows as scoreCols
df_Post101_Psy <- data.frame(item = scoreCols, difficulty = numeric(length(scoreCols)), 
                             discrimination = numeric(length(scoreCols)),
                             difficulty_problematic = character(length(scoreCols)), 
                             discrimination_problematic = character(length(scoreCols)), 
                             overall_problematic = character(length(scoreCols)), 
                             stringsAsFactors = FALSE)

# Loop through each score column
for (i in seq_along(scoreCols)) {
  col <- scoreCols[i]
  
  # Calculate difficulty
  meanScore <- mean(df_Post101[[col]], na.rm = TRUE)
  difficulty <- round(meanScore / fullScore, 2)
  
  # Check if difficulty is problematic
  difficulty_problematic <- ifelse(difficulty < 0.2 | difficulty > 0.8, "problematic", "satisfactory")
  
  # Calculate discrimination
  # Remove the current column from the total score for discrimination calculation
  totalWithoutItem <- totalScorePerChild - df_Post101[[col]]
  
  # Calculate the correlation between the item score and total score without that item
  discrimination <- cor(df_Post101[[col]], totalWithoutItem, use = "complete.obs")
  
  # Check if discrimination is problematic
  discrimination_problematic <- ifelse(discrimination < 0.2, "problematic", "satisfactory")
  
  # 4. Combine the two problems (either difficulty or discrimination is problematic)
  overall_problematic <- ifelse(difficulty_problematic == "problematic" | discrimination_problematic == "problematic", 
                                "problematic", "satisfactory")
  
  # 5. Store results in the pre-allocated dataframe
  df_Post101_Psy$difficulty[i] <- difficulty
  df_Post101_Psy$discrimination[i] <- discrimination
  df_Post101_Psy$difficulty_problematic[i] <- difficulty_problematic
  df_Post101_Psy$discrimination_problematic[i] <- discrimination_problematic
  df_Post101_Psy$overall_problematic[i] <- overall_problematic
}

```

