---
title: "Scoring immediate and delayed post-tests for ep 109"
author: "Kunlei He"
date: "2024-10-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Library
```{r}
library(dplyr)
```

# Load Data
```{r}
# Raw score downloaded from Qualtrics
df_RawPost109 <- read.csv("raw_data/raw_post_109.csv")
df_RawDelayed109 <- read.csv("raw_data/raw_delayed_post_109.csv")

# Manual Score
df_Post109Manual <- read.csv("raw_data/post_109_manual.csv")
df_Delayed109Manual <- read.csv("raw_data/delayed_109_manual.csv")

# Tracker
df_Tracker <- read.csv("clean_data/tracker.csv")
```

# Data Cleaning
## Clean columns and ids
### Immediate post-test
```{r}
# remove unuseful columns
df_Post109 = df_RawPost109[, -c(2:17)]


# remove first two rows
df_Post109 = df_Post109[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Post109$id = ifelse(df_Post109$Intro_4 %in% c(3000:4000), df_Post109$Intro_4, df_Post109$Intro_5)
# get the ra initials
df_Post109$ra = ifelse(is.na(as.numeric(as.character(df_Post109$Intro_4))), df_Post109$Intro_4, df_Post109$Intro_5)
# get rid of intro_4 and intro_5
df_Post109 = df_Post109 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Post109 = df_Post109 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Post109 = df_Post109 %>%  filter(id %in% c(3000:4000))

# find elements in df_Post109$id that are NOT present in df_Tracker$id
diffID = as.numeric(df_Post109$id[!df_Post109$id %in% df_Tracker$id])
print("id in df_Post109 but not in tracker:")
print(diffID) 

# check if they were before the shutdown
print(df_Post109[df_Post109$id %in% diffID, ])
```

### Delayed post-test
```{r}
# remove unuseful columns
df_Delayed109 = df_RawDelayed109[, -c(2:17)]

# remove first two rows
df_Delayed109 = df_Delayed109[-c(1:2), ]

# get the id. Notice the id and ra names are mixed in some cases
df_Delayed109$id = ifelse(df_Delayed109$Intro_4 %in% c(3000:4000), df_Delayed109$Intro_4, df_Delayed109$Intro_5)
# get the ra initials
df_Delayed109$ra = ifelse(is.na(as.numeric(as.character(df_Delayed109$Intro_4))), df_Delayed109$Intro_4, df_Delayed109$Intro_5)
# get rid of intro_4 and intro_5
df_Delayed109 = df_Delayed109 %>% dplyr::select(-Intro_4, -Intro_5)
# rearrange columns
df_Delayed109 = df_Delayed109 %>% dplyr::select(id, ra, everything())

# remove testing ids
df_Delayed109 = df_Delayed109 %>%  filter(id %in% c(3000:4000))

# find elements in df_Tracker$id that are NOT present in df_Post109$id
diffID = as.numeric(df_Tracker$id[!df_Tracker$id %in% df_Delayed109$id])
print("id in df_Delayed109 but not in tracker:")
print(diffID) 
```
## Rename columns
```{r}
colNames109 = c("id", "ra", "start_date", 
                # q1
                "q1_build_init_choice", "q1_build_init_text", "q1_build_rpt_choice", "q1_build_rpt_text",
                # q2
                "q2_race_init_choice", "q2_race_init_text", "q2_race_rpt_choice", "q2_race_rpt_text",
                # q3
                "q3_bird_init_choice", "q3_bird_init_text", "q3_bird_rpt_choice", "q3_bird_rpt_text",
                # q4
                "q4a_try_init_choice", "q4a_try_init_text",
                "q4b_paint_cr", "q4c_cup_cr", "q4d_shape_cr",
                # q5
                "q5a_fish_init_choice", "q5a_fish_init_text", "q5b_fish_cr",
                # q6
                "q6a_shape_init_choice", "q6a_shape_init_text", "q6b_shape_cr",
                # q7
                "q7a_skateboard_init_choice", "q7a_skateboard_init_text", "q7b_skateboard_cr",
                # q8
                "q8_pointy_init_choice", "q8_pointy_init_text", "q8_pointy_rpt_choice", "q8_pointy_rpt_text",
                # q9
                "q9_boxy_init_choice", "q9_boxy_init_text", "q9_boxy_rpt_choice", "q9_boxy_rpt_text",
                # q10
                "q10a_train_cr", "q10b_train_cr",
                # q11
                "q11a_plane_cr", "q11b_plane_cr", "q11c_plane_cr",
                "notes")

# rename
colnames(df_Post109) = colNames109
colnames(df_Delayed109) = colNames109

# convert id to be numeric
df_Delayed109$id = as.numeric(df_Delayed109$id)
df_Post109$id = as.numeric(df_Post109$id)
```

## Handle duplicated ids
### Immediate post-test
```{r}
dupRows_Post109 <- df_Post109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post109)
```

```{r}
# 3425 KH should be 3426
df_Post109 = df_Post109 %>% 
  mutate(id = if_else(id == 3425 & ra == "KH", 3426, id))

# 3437 and 3278 with later dates should be moved to df_Delayed109
## sort by 'id' and 'start_date' in ascending order
df_Post109 <- df_Post109 %>%
  arrange(id, start_date)

## remove duplicate 'id's, keeping the first occurrence
df_Post109 <- df_Post109 %>%
  filter(!duplicated(id))

## separate the removed rows (later dates)
rows_to_move <- df_Post109 %>%
  filter(duplicated(id, fromLast = TRUE))

## append the later rows to 'df_Delayed117'
df_Delayed109 <- bind_rows(df_Delayed109, rows_to_move)

# check dup rows again
dupRows_Post109 <- df_Post109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

print(dupRows_Post109)
```


### Delayed post-test
```{r}
dupRows_Delayed109 <- df_Delayed109 %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()


print(dupRows_Delayed109)
```

# Scoring
Full score for episode 109 is 28
- Non-constructive items full score is 16
- Constructive items full score is 12
## Individual items
### q1_build
```{r}
Func_q1_build_score <- function(df) {
  df$q1_build_init_score = ifelse(grepl("car", df$q1_build_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("car", df$q1_build_init_text, ignore.case = TRUE), 2, 0))

  df$q1_build_rpt_score = ifelse(grepl("car", df$q1_build_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("car", df$q1_build_rpt_text, ignore.case = TRUE), 1, 0))

  df$q1_build_rpt_score = ifelse(df$q1_build_init_score == 2, 0, df$q1_build_rpt_score)
  
  df$q1_build_score = df$q1_build_init_score + df$q1_build_rpt_score
  
  print(paste("The range of q1_build_score is:", 
              min(df$q1_build_score, na.rm = TRUE), "to", 
              max(df$q1_build_score, na.rm = TRUE)))
  
  return (df)
}

df_Post109 <- Func_q1_build_score(df_Post109)
df_Delayed109 <- Func_q1_build_score(df_Delayed109)
```

### q2_race
```{r}
Func_q2_race_score <- function(df) {
  df$q2_race_init_score = ifelse(grepl("slow", df$q2_race_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("slow", df$q2_race_init_text, ignore.case = TRUE), 2, 0))

  df$q2_race_rpt_score = ifelse(grepl("slow", df$q2_race_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("slow", df$q2_race_rpt_text, ignore.case = TRUE), 1, 0))

  df$q2_race_rpt_score = ifelse(df$q2_race_init_score == 2, 0, df$q2_race_rpt_score)
  
  df$q2_race_score = df$q2_race_init_score + df$q2_race_rpt_score
  
  print(paste("The range of q2_race_score is:", 
              min(df$q2_race_score, na.rm = TRUE), "to", 
              max(df$q2_race_score, na.rm = TRUE)))
  
  return (df)
}

df_Post109 <- Func_q2_race_score(df_Post109)
df_Delayed109 <- Func_q2_race_score(df_Delayed109)
```

### q3_bird
```{r}
Func_q3_bird_score <- function(df) {
  df$q3_bird_init_score = ifelse(grepl("point|streamline", df$q3_bird_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("point|streamline", df$q3_bird_init_text, ignore.case = TRUE), 2, 0))

  df$q3_bird_rpt_score = ifelse(grepl("point|streamline", df$q3_bird_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("point|streamline", df$q3_bird_rpt_text, ignore.case = TRUE), 1, 0))

  df$q3_bird_rpt_score = ifelse(df$q3_bird_init_score == 2, 0, df$q3_bird_rpt_score)
  
  df$q3_bird_score = df$q3_bird_init_score + df$q3_bird_rpt_score
  
  print(paste("The range of q3_bird_score is:", 
              min(df$q3_bird_score, na.rm = TRUE), "to", 
              max(df$q3_bird_score, na.rm = TRUE)))
  
  return (df)
}

df_Post109 <- Func_q3_bird_score(df_Post109)
df_Delayed109 <- Func_q3_bird_score(df_Delayed109)
```

### q4_try_cr
```{r}
## This item was a constructive item and manuall scored 
## merge the manual score to the data frame and rename it as q4_try_cr_score

#########################
## Immediate post-test###
#########################
df_Post109 <- df_Post109 %>%
  left_join(df_Post109Manual[c("id", "p109_q4_cr_score")], by = "id") %>%
  mutate(q4_try_cr_score = p109_q4_cr_score) %>%
  select(-p109_q4_cr_score)

print(paste("In immediate post-test, the range of q4_try_cr_score is:", 
              min(df_Post109$q4_try_cr_score, na.rm = TRUE), "to", 
              max(df_Post109$q4_try_cr_score, na.rm = TRUE)))

########################
## Delayed post-test###
#######################
df_Delayed109 <- df_Delayed109 %>%
  left_join(df_Delayed109Manual[c("id", "d109_q4_cr_score")], by = "id") %>%
  mutate(q4_try_cr_score = d109_q4_cr_score) %>%
  select(-d109_q4_cr_score)

print(paste("In delayed post-test, the range of q4_try_cr_score is:", 
              min(df_Delayed109$q4_try_cr_score, na.rm = TRUE), "to", 
              max(df_Delayed109$q4_try_cr_score, na.rm = TRUE)))
```

### q5_fish
```{r}
# q5_fish is the sum of q5_fish_init_score and q5b_fish_cr, which was manually scored
## q5_fish_init_score
Func_q5_fish_score <- function(df) {
  df$q5_fish_init_score = ifelse(grepl("a", df$q5a_fish_init_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("a", df$q5a_fish_init_text, ignore.case = TRUE), 1, 0))
  return (df)
}

df_Post109 <- Func_q5_fish_score(df_Post109)
df_Delayed109 <- Func_q5_fish_score(df_Delayed109)

## q5_fish_cr_score, PAUSED HERE
#########################
## Immediate post-test###
#########################
df_Post109 <- df_Post109 %>%
  left_join(df_Post109Manual[c("id", "p109_q5b_cr_score")], by = "id") %>%
  mutate(q5_fish_cr_score = p109_q5b_cr_score) %>%
  select(-p109_q5b_cr_score)

df_Post109$q5_fish_score = df_Post109$q5_fish_init_score + df_Post109$q5_fish_cr_score

print(paste("In immediate post-test, the range of q5b_fish_cr_score is:", 
              min(df_Post109$q5_fish_score, na.rm = TRUE), "to", 
              max(df_Post109$q5_fish_score, na.rm = TRUE)))

########################
## Delayed post-test###
#######################
df_Delayed109 <- df_Delayed109 %>%
  left_join(df_Delayed109Manual[c("id", "d109_q5b_cr_score")], by = "id") %>%
  mutate(q5_fish_cr_score = d109_q5b_cr_score) %>%
  select(-d109_q5b_cr_score)

df_Delayed109$q5_fish_score = df_Delayed109$q5_fish_init_score + df_Delayed109$q5_fish_cr_score

print(paste("In delayed post-test, the range of q5b_fish_cr_score is:", 
              min(df_Delayed109$q5_fish_score, na.rm = TRUE), "to", 
              max(df_Delayed109$q5_fish_score, na.rm = TRUE)))

```

### q6_shape PENDING

### q7_skateboard PENDING

### q8_pointy
```{r}
Func_q8_pointy_score <- function(df) {
  df$q8_pointy_init_score = ifelse(grepl("fast", df$q8_pointy_init_choice, ignore.case = TRUE), 2,
                                         ifelse(grepl("fast", df$q8_pointy_init_text, ignore.case = TRUE), 2, 0))

  df$q8_pointy_rpt_score = ifelse(grepl("fast", df$q8_pointy_rpt_choice, ignore.case = TRUE), 1,
                                         ifelse(grepl("fast", df$q8_pointy_rpt_text, ignore.case = TRUE), 1, 0))

  df$q8_pointy_rpt_score = ifelse(df$q8_pointy_init_score == 2, 0, df$q8_pointy_rpt_score)
  
  df$q8_pointy_score = df$q8_pointy_init_score + df$q8_pointy_rpt_score
  
  print(paste("The range of q8_pointy_score is:", 
              min(df$q8_pointy_score, na.rm = TRUE), "to", 
              max(df$q8_pointy_score, na.rm = TRUE)))
  
  return (df)
}

df_Post109 <- Func_q8_pointy_score(df_Post109)
df_Delayed109 <- Func_q8_pointy_score(df_Delayed109)

```

### q9_boxy
```{r}
Func_q9_boxy_score <- function(df) {
  # Check for "air" OR "wind" AND "push"
  df$q9_boxy_init_score = ifelse((grepl("air|wind", df$q9_boxy_init_choice, ignore.case = TRUE) & grepl("push", df$q9_boxy_init_choice, ignore.case = TRUE)) | 
                                 (grepl("air|wind", df$q9_boxy_init_text, ignore.case = TRUE) & grepl("push", df$q9_boxy_init_text, ignore.case = TRUE)), 2, 0)

  df$q9_boxy_rpt_score = ifelse((grepl("air|wind", df$q9_boxy_rpt_choice, ignore.case = TRUE) & grepl("push", df$q9_boxy_rpt_choice, ignore.case = TRUE)) | 
                                 (grepl("air|wind", df$q9_boxy_rpt_text, ignore.case = TRUE) & grepl("push", df$q9_boxy_rpt_text, ignore.case = TRUE)), 1, 0)

  # If q9_boxy_init_score is 2, set q9_boxy_rpt_score to 0
  df$q9_boxy_rpt_score = ifelse(df$q9_boxy_init_score == 2, 0, df$q9_boxy_rpt_score)
  
  # Calculate the final q9_boxy_score
  df$q9_boxy_score = df$q9_boxy_init_score + df$q9_boxy_rpt_score
  
  # Print the range of q9_boxy_score
  print(paste("The range of q9_boxy_score is:", 
              min(df$q9_boxy_score, na.rm = TRUE), "to", 
              max(df$q9_boxy_score, na.rm = TRUE)))
  
  return (df)
}

df_Post109 <- Func_q9_boxy_score(df_Post109)
df_Delayed109 <- Func_q9_boxy_score(df_Delayed109)
```

### q10_train_cr
```{r}
## This item was a constructive item and manuall scored
#########################
## Immediate post-test###
#########################
df_Post109 <- df_Post109 %>%
  left_join(df_Post109Manual[c("id", "p109_q10_cr_score")], by = "id") %>%
  mutate(q10_train_cr_score = p109_q10_cr_score) %>%
  select(-p109_q10_cr_score)

print(paste("In immediate post-test, the range of q10_train_cr_score is:", 
              min(df_Post109$q10_train_cr_score, na.rm = TRUE), "to", 
              max(df_Post109$q10_train_cr_score, na.rm = TRUE)))

########################
## Delayed post-test###
#######################
df_Delayed109 <- df_Delayed109 %>%
  left_join(df_Delayed109Manual[c("id", "d109_q10_cr_score")], by = "id") %>%
  mutate(q10_train_cr_score = d109_q10_cr_score) %>%
  select(-d109_q10_cr_score)

print(paste("In delayed post-test, the range of q10_train_cr_score is:", 
              min(df_Delayed109$q10_train_cr_score, na.rm = TRUE), "to", 
              max(df_Delayed109$q10_train_cr_score, na.rm = TRUE)))

```

### q11_plane_cr
```{r}
## This item was a constructive item and manuall scored
#########################
## Immediate post-test###
#########################
df_Post109 <- df_Post109 %>%
  left_join(df_Post109Manual[c("id", "p109_q11_cr_score")], by = "id") %>%
  mutate(q11_plane_cr_score = p109_q11_cr_score) %>%
  select(-p109_q11_cr_score)

print(paste("In immediate post-test, the range of q11_plane_cr_score is:", 
              min(df_Post109$q11_plane_cr_score, na.rm = TRUE), "to", 
              max(df_Post109$q11_plane_cr_score, na.rm = TRUE)))

########################
## Delayed post-test###
#######################

df_Delayed109 <- df_Delayed109 %>%
  left_join(df_Delayed109Manual[c("id", "d109_q11_cr_score")], by = "id") %>%
  mutate(q11_plane_cr_score = d109_q11_cr_score) %>%
  select(-d109_q11_cr_score)

print(paste("In delayed post-test, the range of q11_plane_cr_score is:", 
              min(df_Delayed109$q11_plane_cr_score, na.rm = TRUE), "to", 
              max(df_Delayed109$q11_plane_cr_score, na.rm = TRUE)))

```

## Aggregate scores PENDING
- init_total_score: sum of all the initial responses
- rpt_total_score: sum of all the reprompt responses
- cr_total_score: sum of all the constructive responses
- total_score: sum of all the item scores
- recall_score: sum of all the recall items
- transfer_score: sum of all the transfer items
- narrative_score: sum of all the narrative items
- science_score: sum of all the science-related items

### Immediate post-test
2024-10-11 q6 and q7 are pending
```{r}
# Aggregate all the columns that contain init_score to be init_total_score
df_Post109$p109_init_total_score = rowSums(df_Post109[, grepl("init_score", colnames(df_Post109))], na.rm = TRUE)

# Aggregate all the columns that contain cr_score to be cr_total_score
df_Post109$p109_cr_total_score = rowSums(df_Post109[, grepl("cr_score", colnames(df_Post109))], na.rm = TRUE)

# Aggregate all the columns that contain rpt_score to be rpt_total_score
df_Post109$p109_rpt_total_score = rowSums(df_Post109[, grepl("rpt_score", colnames(df_Post109))], na.rm = TRUE)

# Aggregate all item score to be total_score
df_Post109$p109_total_score = rowSums(df_Post109[, c("q1_build_score", "q2_race_score", "q3_bird_score", 
               "q4_try_cr_score", "q5_fish_score", "q6_shape_score", "q7_skateboard_score", "q8_pointy_score", 
               "q9_boxy_score", "q10_train_cr_score", "q11_plane_cr_score")], na.rm = TRUE)

# Calculate recall and transfer score
## recall items: q1, q2, q3, q4, q8, q9
## transfer items: q5, q6, q7, q10, q11, 
df_Post109$p109_recall_score = rowSums(df_Post109[, c("q1_build_score", "q2_race_score", "q3_bird_score", 
                                                      "q4_try_cr_score", "q8_pointy_score", "q9_boxy_score")], na.rm = TRUE)
df_Post109$p109_transfer_score = rowSums(df_Post109[, c("q5_fish_score", "q6_shape_score", "q7_skateboard_score", 
                                                        "q10_train_cr_score", "q11_plane_cr_score")], na.rm = TRUE)

# Calculate narrative and science score
## narrative items: q1, q2, q4
## science items: q3, q5, q6, q7, q8, q9, q10, q11
df_Post109$p109_narrative_score = rowSums(df_Post109[, c("q1_build_score", "q2_race_score", "q4_try_cr_score")], na.rm = TRUE)
df_Post109$p109_science_score = rowSums(df_Post109[, c("q3_bird_score", "q5_fish_score", "q6_shape_score", 
                                                      "q7_skateboard_score", "q8_pointy_score", "q9_boxy_score", 
                                                      "q10_train_cr_score", "q11_plane_cr_score")], na.rm = TRUE)
```
### Delayed post-test
2024-10-11 q6 and q7 are pending
```{r}
# Aggregate all the columns that contain init_score to be init_total_score
df_Delayed109$d109_init_total_score = rowSums(df_Delayed109[, grepl("init_score", colnames(df_Delayed109))], na.rm = TRUE)

# Aggregate all the columns that contain cr_score to be cr_total_score
df_Delayed109$d109_cr_total_score = rowSums(df_Delayed109[, grepl("cr_score", colnames(df_Delayed109))], na.rm = TRUE)

# Aggregate all the columns that contain rpt_score to be rpt_total_score
df_Delayed109$d109_rpt_total_score = rowSums(df_Delayed109[, grepl("rpt_score", colnames(df_Delayed109))], na.rm = TRUE)

# Aggregate all item score to be total_score
df_Delayed109$d109_total_score = rowSums(df_Delayed109[, c("q1_build_score", "q2_race_score, q3_bird_score, q4_try_cr_score, q5_fish_score, q6_shape_score, q7_skateboard_score, q8_pointy_score, q9_boxy_score, q10_train_cr_score, q11_plane_cr_score")], na.rm = TRUE)

# Calculate recall and transfer score
## recall items: q1, q2, q3, q4, q8, q9
## transfer items: q5, q6, q7, q10, q11, 
df_Delayed109$d109_recall_score = rowSums(df_Delayed109[, c("q1_build_score", "q2_race_score", "q3_bird_score", 
                                                      "q4_try_cr_score", "q8_pointy_score", "q9_boxy_score")], na.rm = TRUE)
df_Delayed109$d109_transfer_score = rowSums(df_Delayed109[, c("q5_fish_score", "q6_shape_score", "q7_skateboard_score", 
                                                        "q10_train_cr_score", "q11_plane_cr_score")], na.rm = TRUE)

# Calculate narrative and science score
## narrative items: q1, q2, q4
## science items: q3, q5, q6, q7, q8, q9, q10, q11
df_Delayed109$d109_narrative_score = rowSums(df_Delayed109[, c("q1_build_score", "q2_race_score", "q4_try_cr_score")], na.rm = TRUE)
df_Delayed109$d109_science_score = rowSums(df_Delayed109[, c("q3_bird_score", "q5_fish_score", "q6_shape_score", 
                                                      "q7_skateboard_score", "q8_pointy_score", "q9_boxy_score", 
                                                      "q10_train_cr_score", "q11_plane_cr_score")], na.rm = TRUE)
```

# Write to file
```{r}
write.csv(df_Post109, "clean_data/post_109_scored.csv", row.names = FALSE)
write.csv(df_Delayed109, "clean_data/delayed_109_scored.csv", row.names = FALSE)
```

# Psychometric Analysis
Metrics: 
- difficulty = (mean score / total score per item) * 100
  - problematic if less than 0.2 or greater than 0.8
- discrimination =  the correlation between the item score and the total score without that item for each child
  - problematic if less than 0.2

## Immediate post-test
```{r}
# Load the data
# df_Post109 <- read.csv("clean_data/post_109_scored.csv")

# List of score columns - NEEDS TO ADD BACK q6_shape_score, q7_skateboard_score ONCE SCORING IS DONE
scoreCols <- c("q1_build_score", "q2_race_score", "q3_bird_score", 
               "q4_try_cr_score", "q5_fish_score", "q8_pointy_score", 
               "q9_boxy_score", "q10_train_cr_score", "q11_plane_cr_score")

# List of columns that are CR items (full score = 12)
crItems <- c("q4_try_cr_score", "q10_train_cr_score", "q11_plane_cr_score")

# Full score for other items (not CR items)
nonCrFullScore <- 2
crFullScore <- 4

# Calculate total score for discrimination (sum of all items per respondent)
totalScorePerChild <- rowSums(df_Post109[scoreCols], na.rm = TRUE)

# Create an empty dataframe to store the results with the same number of rows as scoreCols
df_Post109_Psy <- data.frame(item = scoreCols, difficulty = numeric(length(scoreCols)), 
                             discrimination = numeric(length(scoreCols)),
                             difficulty_problematic = character(length(scoreCols)), 
                             discrimination_problematic = character(length(scoreCols)), 
                             overall_problematic = character(length(scoreCols)), 
                             stringsAsFactors = FALSE)

# Loop through each score column
for (i in seq_along(scoreCols)) {
  col <- scoreCols[i]
  
  # 1. Determine the full score based on whether the item is CR or not
  if (col %in% crItems) {
    fullScore <- crFullScore
  } else {
    fullScore <- nonCrFullScore
  }
  
  # 2. Calculate difficulty
  meanScore <- mean(df_Post109[[col]], na.rm = TRUE)
  difficulty <- round(meanScore / fullScore, 2)
  
  # Check if difficulty is problematic
  difficulty_problematic <- ifelse(difficulty < 0.2 | difficulty > 0.8, "problematic", "satisfactory")
  
  # 3. Calculate discrimination
  # Remove the current column from the total score for discrimination calculation
  totalWithoutItem <- totalScorePerChild - df_Post109[[col]]
  
  # Calculate the correlation between the item score and total score without that item
  discrimination <- cor(df_Post109[[col]], totalWithoutItem, use = "complete.obs")
  
  # Check if discrimination is problematic
  discrimination_problematic <- ifelse(discrimination < 0.2, "problematic", "satisfactory")
  
  # 4. Combine the two problems (either difficulty or discrimination is problematic)
  overall_problematic <- ifelse(difficulty_problematic == "problematic" | discrimination_problematic == "problematic", 
                                "problematic", "satisfactory")
  
  # 5. Store results in the pre-allocated dataframe
  df_Post109_Psy$difficulty[i] <- difficulty
  df_Post109_Psy$discrimination[i] <- discrimination
  df_Post109_Psy$difficulty_problematic[i] <- difficulty_problematic
  df_Post109_Psy$discrimination_problematic[i] <- discrimination_problematic
  df_Post109_Psy$overall_problematic[i] <- overall_problematic
}

```

## Delayed post-test
```{r}
# Load the data
# df_Delayed109 <- read.csv("clean_data/Delayed_109_scored.csv")

# List of score columns - NEEDS TO ADD BACK q6_shape_score, q7_skateboard_score ONCE SCORING IS DONE
scoreCols <- c("q1_build_score", "q2_race_score", "q3_bird_score", 
               "q4_try_cr_score", "q5_fish_score", "q8_pointy_score", 
               "q9_boxy_score", "q10_train_cr_score", "q11_plane_cr_score")

# List of columns that are CR items (full score = 12)
crItems <- c("q4_try_cr_score", "q10_train_cr_score", "q11_plane_cr_score")

# Full score for other items (not CR items)
nonCrFullScore <- 2
crFullScore <- 4

# Calculate total score for discrimination (sum of all items per respondent)
totalScorePerChild <- rowSums(df_Delayed109[scoreCols], na.rm = TRUE)

# Create an empty dataframe to store the results with the same number of rows as scoreCols
df_Delayed109_Psy <- data.frame(item = scoreCols, difficulty = numeric(length(scoreCols)), 
                             discrimination = numeric(length(scoreCols)),
                             difficulty_problematic = character(length(scoreCols)), 
                             discrimination_problematic = character(length(scoreCols)), 
                             overall_problematic = character(length(scoreCols)), 
                             stringsAsFactors = FALSE)

# Loop through each score column
for (i in seq_along(scoreCols)) {
  col <- scoreCols[i]
  
  # 1. Determine the full score based on whether the item is CR or not
  if (col %in% crItems) {
    fullScore <- crFullScore
  } else {
    fullScore <- nonCrFullScore
  }
  
  # 2. Calculate difficulty
  meanScore <- mean(df_Delayed109[[col]], na.rm = TRUE)
  difficulty <- round(meanScore / fullScore, 2)
  
  # Check if difficulty is problematic
  difficulty_problematic <- ifelse(difficulty < 0.2 | difficulty > 0.8, "problematic", "satisfactory")
  
  # 3. Calculate discrimination
  # Remove the current column from the total score for discrimination calculation
  totalWithoutItem <- totalScorePerChild - df_Delayed109[[col]]
  
  # Calculate the correlation between the item score and total score without that item
  discrimination <- cor(df_Delayed109[[col]], totalWithoutItem, use = "complete.obs")
  
  # Check if discrimination is problematic
  discrimination_problematic <- ifelse(discrimination < 0.2, "problematic", "satisfactory")
  
  # 4. Combine the two problems (either difficulty or discrimination is problematic)
  overall_problematic <- ifelse(difficulty_problematic == "problematic" | discrimination_problematic == "problematic", 
                                "problematic", "satisfactory")
  
  # 5. Store results in the pre-allocated dataframe
  df_Delayed109_Psy$difficulty[i] <- difficulty
  df_Delayed109_Psy$discrimination[i] <- discrimination
  df_Delayed109_Psy$difficulty_problematic[i] <- difficulty_problematic
  df_Delayed109_Psy$discrimination_problematic[i] <- discrimination_problematic
  df_Delayed109_Psy$overall_problematic[i] <- overall_problematic
}
```

